---
title: "Cultivar Results Review"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(8, 4))
```

\newpage

```{r include=FALSE, message=F}
library(sf)
library(sp)
library(rgdal)
require(tidyverse)
require(reshape2)
require(ggpubr)
library(knitr)


path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/chmu/" 
path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_cultivarRESULTS/" 

period <- 1989:2019 # time period


# crop <- "ALFA"
# crop <- "BARL"
# crop <- "CSIL"
# crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
crop <- "WWHT"


# crop ID + seasonality

if(crop == "ALFA"){
    cropid <- 31 
    cropname <- "alfalfa"
    seas <- "OTH"
  } else if (crop == "BARL"){
    cropid <- 14
    cropname <- "spring barley"
    seas <- "SPG"
  } else if (crop == "CSIL"){
    cropid <- 29
    cropname <- "corn silage"
    seas <- "SPG"
  } else if (crop == "CORN"){
    cropid <- 2
    cropname <- "corn"
    seas <- "SPG"
  } else if (crop == "OATS"){
    cropid <- 16
    cropname <- "oat"
    seas <- "SPG"
  } else if (crop == "FPEA"){
    cropid <- 26
    cropname <- "field peas"
    seas <- "SPG"
  } else if (crop == "POTA"){
    cropid <- 51
    cropname <- "potatoes"
    seas <- "SPG"
  } else if (crop == "RAPE"){
    cropid <- 122
    cropname <- "winter rapeseed"
    seas <- "WIN"
  } else if (crop == "RYE") {
    cropid <- 19
    cropname <- "rye"
    seas <- "WIN"
  } else if (crop == "SGBT"){
    cropid <- 62
    cropname <- "sugarbeet"
    seas <- "SPG"
  } else if (crop == "SUNF"){
    cropid <- 7
    cropname <- "sunflower"
    seas <- "SPG"
  } else if (crop == "SOYB"){
    cropid <- 1
    cropname <- "soybean"
    seas <- "SPG"
  } else if (crop == "WWHT"){
    cropid <- 10
    cropname <- "winter wheat"
    seas <- "WIN"
  } else {
    print("ZEROO")
}

# WCY parameter (fraction water in yield ) WCY = 0.12 -> yield + wcy -> 1.12

wcy <- case_when(crop %in% c("ALFA", "BARL", "FPEA", "RYE", "WWHT") ~ 1.12,
                 crop %in% c("CSIL", "CORN") ~ 1.15, 
                 crop %in% c("OATS") ~ 1.10, 
                 crop %in% c("POTA") ~ 1.8, 
                 crop %in% c("SGBT") ~ 1.84, 
                 crop %in% c("SUNF") ~ 1.06, 
                 crop %in% c("SOYB") ~ 1.13) 
```

\newpage

# CROP CULTIVARS

```{r}

print(cropname)

# *** READ *** READ *** READ ** READ ***
phu_cal_grid <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal_grid.csv"), header = TRUE, sep = ";")
jul_cal <- read.table(paste0(path_tab, "jul_cal.csv"), header = TRUE, sep = ";")
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")


acm <- read.table(paste0(path_out, crop, "/_simulated/ACM_msacc.txt"), header = T, sep = ";")
acy <- read.table(paste0(path_out, crop, "/_simulated/ACY_msacc.txt"), header = T, sep = ";")
# *** READ *** READ *** READ ** READ ***

outtab0 <- merge(acm, acy, all = T) 
outtab <- merge(outtab0, phu_cal_grid, by.x = "runid", by.y = "runid") # join ACM and ACY with SCENARIO
outtab$YLDG <- (outtab$YLDG*wcy) # WCY parameter / fraction water in yield 
outtab <- outtab %>%
  mutate(PO = case_when(KLIMREG == 0 ~ "K",
                        KLIMREG %in% c(1:3) ~ "R",
                        KLIMREG %in% c(4:5) ~ "C",
                        KLIMREG %in% c(6:7) ~ "B",
                        KLIMREG %in% c(8:9) ~ "H"))

# rm(acm)
# rm(acy)
# rm(phu_cal_grid)
# rm(outtab0)
  
```


```{r results='asis'}

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")
   # cat('\n')
   # cat("This is a heading for ", croplist[i] , "\n")
   # kable(cultivars, caption = paste0("Cultivars of ", cropname))
   # cat('\n')
   tab <- kable(cultivars, caption = paste0("Cultivars of ", cropname))
   print(tab)

```

\newpage

# YIELD

## AVERAGE SIMULATED YIELD FOR EVERY SCENARIO

```{r}
out_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, PRCP, PET, TS) %>% 
  group_by(runid) %>% 
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPRCP = mean(PRCP), 
            avgPET = mean(PET), avgTS = mean(TS)) %>% 
  distinct()

scen_list <- levels(as.factor(out_scen$scenario))
# print(scen_list)

```


```{r results='asis'}

for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(out_scen, scenario == scene)
  gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)
  mout <-sp::merge(filt_scen, gridmap, by = "GRID_NO")
  ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
    geom_sf()+
    ggtitle(paste0("Average yield of ", cropname, " in 1989-2019 / scenario: ", scene )) + 
    scale_fill_gradient("[t/ha]", 
    low = "yellow",
    high = "darkgreen",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill", 
    limits = c(1.2,4.8))+ # !!!!!!!!!!!!!!!! adjust
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_yld)
}
```


## INSPECTING SINGLE GRID

Checking simulated yield levels in a single selected grid

```{r}

g1 <- out_scen %>% 
  filter(GRID_NO == 1)
print(g1, n=27)

g50 <- out_scen %>% 
  filter(GRID_NO == 50)
print(g50, n=27)

g167 <- out_scen %>% 
  filter(GRID_NO == 167)
print(g167, n=27)
```

\newpage

## DESCRIPTIVE STATISTICS

descriptive statistics for each grid
calculated from all `r nrow(cultivars)` cultivars

```{r}
destat <- outtab %>% 
select(runid, YR, scenario, GRID_NO, YLDG) %>% 
  group_by(GRID_NO) %>% 
  summarise(GRID_NO, minYLD = min(YLDG), maxYLD = max(YLDG),
            avgYLD = mean(YLDG), sdYLD = sd(YLDG)) %>% 
  mutate(ranYLD = maxYLD-minYLD) %>% 
  distinct()

# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)

desshp <-sp::merge(destat, gridmap, by = "GRID_NO")

```

### mean

```{r}
ggplot(desshp, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Mean simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                     high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
```


### range

```{r}

ggplot(desshp, aes(geometry = geometry, fill= ranYLD))+
  geom_sf()+
  ggtitle(paste0("Range of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

### sd

```{r}
ggplot(desshp, aes(geometry = geometry, fill= sdYLD))+
  geom_sf()+
  ggtitle(paste0("Standard deviation of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "red",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
```



\newpage

# SELECTING SCENARIO

criteria: 

* highest yield

* lowest IHVD shift

* lowest IPLD shift

working DF: **dat_shft**

## IHVD + IPLD

IPLD and IHVD dates shifted compared to the dates given by cultivar setup

calculate the shift

sum IPLD and IHVD shift

picks scenario with the lowest number of days

**selected:**


```{r preparing DF with calculated shifts, message=FALSE}

# marge output table with designed cultivar

outtab <- if(crop == "WWHT"){
  filter(outtab, IHVD != 0)
}



hvd_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, IPLD, IGMD, IHVD) %>% 
  merge(cultivars, by.x = "scenario", by.y = "runid") %>% 
  mutate(gIPLD = paste0(YR, sprintf("%02d", PLN_MON), sprintf("%02d", PLN_DAY))) %>% # given IPLD
  mutate(gIHVD = paste0(YR, sprintf("%02d", HRV_MON), sprintf("%02d", HRV_DAY))) # given IHVD

# formatting date

hvd_scen$IPLD <- as.Date(as.character(hvd_scen$IPLD), format = "%Y%m%d")
hvd_scen$IHVD <- as.Date(as.character(hvd_scen$IHVD), format = "%Y%m%d")

hvd_scen$gIPLD <- as.Date(hvd_scen$gIPLD, format = "%Y%m%d")
hvd_scen$gIHVD <- as.Date(hvd_scen$gIHVD, format = "%Y%m%d")

# difference of IPLD and IHVD in days

hvd_scen$p_diff <- as.numeric(difftime(hvd_scen$gIPLD, hvd_scen$IPLD, units = "days"))
hvd_scen$h_diff <- as.numeric(difftime(hvd_scen$gIHVD, hvd_scen$IHVD, units = "days"))

# avg date shift for scenario

dat_shft <- hvd_scen %>% 
  group_by(runid) %>%
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPshft = mean(p_diff), avgHshft = mean(h_diff)) %>% # avgPRCP = mean(PRCP), avgPET = mean(PET), avgTS = mean(TS)
  distinct() %>% 
  mutate(H = abs(avgHshft)) %>% 
  mutate(P = abs(avgPshft)) %>% 
  mutate(HPsum = H+P) # sum of P and H days
  
# pick scenario

selHP <- dat_shft %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(HPsum)) 
 
# filter(dat_shft, GRID_NO == 497)
# filter(pick, GRID_NO == 497) # only check

selHP$scenario <- as.factor(selHP$scenario)
summary(selHP$scenario)
```


```{r}
gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)
mout <-sp::merge(selHP, gridmap, by = "GRID_NO")
ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)
```


## YIELD + IHVD

scenario with the lowest IHVD shift and highest yield

**selected:**

```{r}
selHY <- dat_shft %>% 
  group_by(GRID_NO) %>%
  filter(H == min(H)) %>%
  filter(avgYLD == max(avgYLD))
  # slice(which.min(HPsum)) 
 
# filter(dat_shft, GRID_NO == 497)
# filter(pick, GRID_NO == 497) # only check

selHY$scenario <- as.factor(selHY$scenario)
summary(selHY$scenario)

```
```{r}
gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)
mout <-sp::merge(selHY, gridmap, by = "GRID_NO")
ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)
```

