---
title: "EPIC harvest Cultivars"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

\newpage 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(8, 4))

# install.packages("tidyverse", dependencies = T)
# install.packages("gdata")
require(tidyverse)
require(gdata) # write.fwf
library(sf)
library(sp)
library(rgdal)
require(reshape2)
require(ggpubr)
library(knitr)

```

# INITIAL SETUP

## paths 

```{r echo = T}
path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/v3_czsk/" 
path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_cultivarRESULTS/" 

```

## time period

```{r echo = T}
period <- 1989:2019 
```



## crop params

```{r}

# crop <- "ALFA"
# crop <- "BARL"
# crop <- "CSIL"
# crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
crop <- "WWHT"


# crop ID + seasonality

if(crop == "ALFA"){
    cropid <- 31 
    cropname <- "alfalfa"
    seas <- "OTH"
  } else if (crop == "BARL"){
    cropid <- 14
    cropname <- "spring barley"
    seas <- "SPG"
  } else if (crop == "CSIL"){
    cropid <- 29
    cropname <- "corn silage"
    seas <- "SPG"
  } else if (crop == "CORN"){
    cropid <- 2
    cropname <- "corn"
    seas <- "SPG"
  } else if (crop == "OATS"){
    cropid <- 16
    cropname <- "oat"
    seas <- "SPG"
  } else if (crop == "FPEA"){
    cropid <- 26
    cropname <- "field peas"
    seas <- "SPG"
  } else if (crop == "POTA"){
    cropid <- 51
    cropname <- "potatoes"
    seas <- "SPG"
  } else if (crop == "RAPE"){
    cropid <- 122
    cropname <- "winter rapeseed"
    seas <- "WIN"
  } else if (crop == "RYE") {
    cropid <- 19
    cropname <- "rye"
    seas <- "WIN"
  } else if (crop == "SGBT"){
    cropid <- 62
    cropname <- "sugarbeet"
    seas <- "SPG"
  } else if (crop == "SUNF"){
    cropid <- 7
    cropname <- "sunflower"
    seas <- "SPG"
  } else if (crop == "SOYB"){
    cropid <- 1
    cropname <- "soybean"
    seas <- "SPG"
  } else if (crop == "WWHT"){
    cropid <- 10
    cropname <- "winter wheat"
    seas <- "WIN"
  } else {
    print("ZEROO")
}


# WCY parameter (fraction water in yield ) WCY = 0.12 -> yield + wcy -> 1.12

# ??? RAPE ???

wcy <- case_when(crop %in% c("ALFA", "BARL", "FPEA", "RYE", "WWHT") ~ 1.12,
                 crop %in% c("CSIL", "CORN") ~ 1.15, 
                 crop %in% c("OATS") ~ 1.10, 
                 crop %in% c("POTA") ~ 1.8, 
                 crop %in% c("SGBT") ~ 1.84, 
                 crop %in% c("SUNF") ~ 1.06, 
                 crop %in% c("SOYB") ~ 1.13) 
```
* crop: `r crop`

* crop ID: `r cropid`

* crop name: `r cropname`

* seasonality: `r seas`

* WCY parameter: `r wcy`

\newpage 

# HARVEST OUTPUT FILES (in progress)

## ACM

output file stored in 'EPIC0810'

?

```{r eval=FALSE}

# load ACM files without 11 lines of header and save it as csv

acmnames <- list.files(path_epic, pattern= "\\.ACM$")  # Identify file names
acmnamesWO <- tools::file_path_sans_ext(acmnames) # remove the extension '.ACM'

for(i in 1:length(acmnames)) {
  a <- read.table(paste0(path_epic, acmnames[i]), header = FALSE, skip = 11)
  a$source <- paste0(acmnamesWO[i])
  dir.create (paste0(path_out, crop, "/_simulated/ACM"), showWarnings = FALSE)
  write.csv(a, file = paste0(path_out, crop, "/_simulated/ACM/", acmnamesWO[i], ".csv"))
}


# read csv and bind them into one single file


acmcomb <- list.files(path = paste0(path_out, crop, "/_simulated/ACM"),     # https://statisticsglobe.com/merge-csv-files-in-rhttps://statisticsglobe.com/merge-csv-files-in-r
                      pattern = "*.csv", full.names = TRUE) %>%  # Identify all csv files in folder
  lapply(read_csv) %>%                                            # Store all files in list
  bind_rows                                                       # Combine data sets into one data set


# rename header

col_names_acm <- c("X", "YR",  "RT", "PRCP", "PET", "ET ", "Q", "SSF", "PRK", "CVF", "MUSS", "YW", "GMN", "NMN", "NFIX", "NITR", "AVOL",
                   "DN", "YON", "QNO3", "SSFN", "PRKN", "MNP", "YP", "QAP", "PRKP", "LIME", "OCPD", "TOC", "APBC", "TAP", "TNO3", "SimUID")
names(acmcomb) <- col_names_acm


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acmcomb, file = paste0(path_out, "_simulated/", currentDate, "_", crop, "_acm.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```

## ACY

output file stored in 'EPIC0810'

?

```{r eval=F}

# load ACY files without 11 lines of header and save it as csv

acynames <- list.files(path_in, pattern= "\\.ACY$")  # Identify file names
acynamesWO <- tools::file_path_sans_ext(acynames) # remove the extension '.ACM'


for(i in 1:length(acynames)) {
  a <- read.table(paste0(path_epic, acynames[i]), header = FALSE, skip = 11)
  a$source <- paste0(acynamesWO[i])
  dir.create (paste0(path_out, crop, "/_simulated/ACY"), showWarnings = FALSE)
  write.csv(a, file = paste0(path_out, crop, "/_simulated/ACY/", acynamesWO[i], ".csv"))
}


# read csv and bind them into one single file


acycomb <- list.files(path = paste0(path_out, crop, "/_simulated/ACY"),     # https://statisticsglobe.com/merge-csv-files-in-rhttps://statisticsglobe.com/merge-csv-files-in-r
                      pattern = "*.csv", full.names = TRUE) %>%  # Identify all csv files in folder
  lapply(read_csv) %>%                                            # Store all files in list
  bind_rows                                                       # Combine data sets into one data set


# rename header

col_names_acy <- c("X", "YR",  "RT", "CPNM", "YLDG", "YLDF ", "BIOM", "YLN", "YLP", "FTN", "FTP", "IRGA", "IRDL",
                   "WUEF", "GSET", "CAW", "CRF", "CQV", "COST", "COOP", "RYLG", "RYLF", "PSTF", "WS", "NS", "PS",
                   "KS", "TS", "AS", "SS", "PPOP", "IPLD", "IGMD", "IHVD", "SimUID")
names(acycomb) <- col_names_acy


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acycomb, file = paste0(path_out, "_simulated/", currentDate, "_", crop, "_acy.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```



## OUTPUT TABLE

```{r}

# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal.csv"), header = TRUE, sep = ";")
jul_cal <- read.table(paste0(path_tab, "jul_cal.csv"), header = TRUE, sep = ";")
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")


# acm <- read.table(paste0(path_out, crop, "/_simulated/ACM_msacc.txt"), header = T, sep = ";")
# acy <- read.table(paste0(path_out, crop, "/_simulated/ACY_msacc.txt"), header = T, sep = ";")

# OR ?
  
if (seas == "SPG"){
  acm <- read.table(paste0(path_out, crop, "/_simulated/ACM_msacc.txt"), header = T, sep = ";")
}  else if (seas == "WIN"){
  acm <- read.table(paste0(path_out, crop, "/_simulated/ACM_msacc.txt"), header = T, sep = ";") %>%
  filter(YR != 1989)
} else {
  print("ZEROO")
}

if (seas == "SPG"){
  acy <- read.table(paste0(path_out, crop, "/_simulated/ACY_msacc.txt"), header = T, sep = ";")
}  else if (seas == "WIN"){
  acy <- read.table(paste0(path_out, crop, "/_simulated/ACY_msacc.txt"), header = T, sep = ";") %>%
  filter(IHVD != 0)
} else {
  print("ZEROO")
}



# *** READ *** READ *** READ ** READ ***


# merge ACM and ACY; apply WCY parameter

outtab0 <- merge(acm, acy) %>% 
  filter(YR != 1989)
outtab <- merge(outtab0, phu_cal, by.x = "runid", by.y = "runid") # join ACM and ACY with SCENARIO
outtab$YLDG <- (outtab$YLDG*wcy) # WCY parameter / fraction water in yield 
# outtab <- outtab %>%
#   mutate(PO = case_when(KLIMREG == 0 ~ "K",
#                         KLIMREG %in% c(1:3) ~ "R",
#                         KLIMREG %in% c(4:5) ~ "C",
#                         KLIMREG %in% c(6:7) ~ "B",
#                         KLIMREG %in% c(8:9) ~ "H"))

rm(acm)
rm(acy)
rm(phu_cal)
rm(outtab0)


# outtab == output tables; YLDG corrected with WCY parameter

```


\newpage 

# CULTIVARS REVIEW

## CULTIVARS

```{r results='asis'}

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")
   # cat('\n')
   # cat("This is a heading for ", croplist[i] , "\n")
   # kable(cultivars, caption = paste0("Cultivars of ", cropname))
   # cat('\n')
   tab <- kable(cultivars, caption = paste0("Cultivars of ", cropname))
   print(tab)

```

## MAP YIELD FOR ALL SCENARIOS

```{r results='asis'}

out_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, PRCP, PET, TS) %>% 
  group_by(runid) %>% 
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPRCP = mean(PRCP), 
            avgPET = mean(PET), avgTS = mean(TS)) %>% 
  distinct()

scen_list <- levels(as.factor(out_scen$scenario))
# print(scen_list)

for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(out_scen, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
    geom_sf()+
    ggtitle(paste0("Average yield of ", cropname, " in 1989-2019 / scenario: ", scene )) + 
    scale_fill_gradient("[t/ha]", 
    low = "yellow",
    high = "darkgreen",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill", 
    limits = c(3,9))+ # !!!!!!!!!!!!!!!! WHE
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_yld)
}

```

## DESCRIPTIVE STATISTICS

descriptive statistics for each grid
calculated from all `r nrow(cultivars)` cultivars

```{r}
destat <- outtab %>% 
select(runid, YR, scenario, GRID_NO, YLDG) %>% 
  group_by(GRID_NO) %>% 
  summarise(GRID_NO, minYLD = min(YLDG), maxYLD = max(YLDG),
            avgYLD = mean(YLDG), sdYLD = sd(YLDG)) %>% 
  mutate(ranYLD = maxYLD-minYLD) %>% 
  distinct()

# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)

desshp <-sp::merge(destat, gridmap, by.x = "GRID_NO", by.y = "GRID")

# mean

ggplot(desshp, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Mean simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                     high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# range

ggplot(desshp, aes(geometry = geometry, fill= ranYLD))+
  geom_sf()+
  ggtitle(paste0("Range of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# sd

ggplot(desshp, aes(geometry = geometry, fill= sdYLD))+
  geom_sf()+
  ggtitle(paste0("Standard deviation of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "red",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

```

\newpage 

# PLANTING, GERMINATION AND HARVEST DATE SHIFTS

criteria: 

* given IPLD and IPLD shift (0-2; 3-10; >10)

* IPLD and IGMD shift (0-5; 5-10; >10)

* given IHVD and IHVD shift (0-7; 7-14; >14)

working DF: **shifts**

working DF: **avg_shifts**


```{r preparing DF with calculated shifts, message=FALSE}


# merge output table with designed cultivar

outtab <- if(crop == "WWHT"){
  filter(outtab, IHVD != 0)
} else {outtab <- outtab}


shifts <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, IPLD, IGMD, IHVD) %>% 
  merge(cultivars, by.x = "scenario", by.y = "runid") %>% 
  mutate(gIPLD = paste0(YR, sprintf("%02d", PLN_MON), sprintf("%02d", PLN_DAY))) %>% # given IPLD
  mutate(gIHVD = paste0(YR, sprintf("%02d", HRV_MON), sprintf("%02d", HRV_DAY))) # given IHVD
  

# formatting date

shifts$IPLD <- as.Date(as.character(shifts$IPLD), format = "%Y%m%d")
shifts$gIPLD <- as.Date(shifts$gIPLD, format = "%Y%m%d")

shifts$IGMD <- as.Date(as.character(shifts$IGMD), format = "%Y%m%d")

shifts$IHVD <- as.Date(as.character(shifts$IHVD), format = "%Y%m%d")
shifts$gIHVD <- as.Date(shifts$gIHVD, format = "%Y%m%d")


# differences 

shifts$shft_IPLD <- as.numeric(difftime(shifts$gIPLD, shifts$IPLD, units = "days"))
shifts$shft_IGMD <- as.numeric(difftime(shifts$IGMD, shifts$IPLD, units = "days"))
shifts$shft_IHVD <- as.numeric(difftime(shifts$gIHVD, shifts$IHVD, units = "days"))

if(seas == "WIN"){
  shifts$shft_IPLD <- case_when(shifts$shft_IPLD >= 365 ~ 0,
                                shifts$shft_IPLD != 365 ~ shifts$shft_IPLD)
} else {
  shifts$shft_IPLD <- shifts$shft_IPLD
}

# avg date shift for scenario

avg_shifts <- shifts %>% 
  group_by(runid) %>%
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPshft = mean(shft_IPLD), avgGshft = mean(shft_IGMD), 
            avgHshft = mean(shft_IHVD)) %>% # avgPRCP = mean(PRCP), avgPET = mean(PET), avgTS = mean(TS)
  distinct()
```

## IPLD

```{r}

for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IPLD <- ggplot(mout, aes(geometry = geometry, fill= avgPshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IPLD and actual IPLD for ", cropname, " / scenario: ", scene)) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    # limits = c(-60,30))+ #CORN
    limits = c(-10,10))+ #WWHT
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IPLD)
}
```

## IGMD


```{r}
for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgGshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of IGMD from IPLD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = c(-30,30))+ #CORN, WWHT
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

## IHVD

```{r}
for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgHshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IHVD and actual IHVD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    # limits = c(-100,10))+ #CORN
    limits = c(-5,5))+ #WWHT
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

\newpage

# SELECTING SCENARIO

## BASED ON IPLD

```{r}

selIPLD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgPshft)))
 

selIPLD$scenario <- as.factor(selIPLD$scenario)
summary(selIPLD$scenario)

```

```{r results='asis'}
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIPLD$scenario

IPLD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IPLD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IPLD"))
print(tab)
```


```{r}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIPLD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IPLD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)

```

## BASED ON IGMD

```{r}

selIGMD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgGshft)))
 

selIGMD$scenario <- as.factor(selIGMD$scenario)
summary(selIGMD$scenario)

```

```{r results='asis'}
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIGMD$scenario

IGMD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IGMD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IGMD"))
print(tab)
```

```{r}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIGMD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IGMD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```

## BASED ON IHVD

```{r}

selIHVD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgHshft)))
 

selIHVD$scenario <- as.factor(selIHVD$scenario)
summary(selIHVD$scenario)

```

```{r results='asis'}
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIHVD$scenario

IHVD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IHVD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IHVD"))
print(tab)
```

```{r}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIHVD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IHVD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```



```{r RENDER, eval=F}

# install.packages("rmarkdown")
# library(rmarkdown)
# rmarkdown::render(input = "EPIC_hrvCult.Rmd", 
#        output_format = "pdf_document",
#        output_file = paste0("c:/Users/krizovak/Documents/__EPIC__/R/markdown/reports/", crop, "_hrvCultReport.pdf"))

```

