---
title: 'EPIC-IIASA (CZ) :: v3 :: manual'
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

\newpage 

# VERSIONS OF EPIC-IIASA (CZ)

* v0 : RS
* v1 : KK at IIASA, 2021
* v2 : KK at IIASA, 2022
* v3 : KK at IIASA, 2022; CZ + SK
* v4 : KK at IIASA, 2022; CZ + SK; 8 parallels


\newpage 

# CROPS

## Selected crops for CZ and SK

### Alfalfa

* crop "ALFA"
* crop ID = 31 
* seasonality = other

### Spring barley

* crop "BARL"
* crop ID = 14 
* seasonality = spring

### Corn silage

* crop "CSIL"
* crop ID = 29 
* seasonality = spring

### Corn 

* crop "CORN"
* crop ID = 2 
* seasonality = spring

### Oats 

* crop "OATS"
* crop ID = 16 
* seasonality = spring

### Field peas 

* crop "FPEA"
* crop ID = 26
* seasonality = spring

### Potato

* crop "FPEA"
* crop ID = 51
* seasonality = spring

### Winter rapeseed 

* crop "RAPE"
* crop ID = 122
* seasonality = winter

### Rye

* crop "RYE"
* crop ID = 19
* seasonality = winter

### Sugar beet 

* crop "SGBT"
* crop ID = 62
* seasonality = spring

### Sunflower 

* crop "SUNF"
* crop ID = 7
* seasonality = spring

### Soybeans 

* crop "SOYB"
* crop ID = 1
* seasonality = spring

### Winter wheat

* crop "WWHT"
* crop ID = 10
* seasonality = winter


\newpage

# R and RMD SCRIPTS

Naming rules:


* **CHMU_** : manipulation with chmu data (CZ)
* **CGMS_** : interpolation of chmu data (CZ)
* **EPIC_** : scripts used directly for generating or harvesting EPIC files
* **PROC_** : processing scripts, short, usually one time runs
* **VISUALS_** : outputs visualisation scripts

* **_runCult** : run on cultivars, BEFORE EPIC simulations
* **_runCrop** : run on crop, BEFORE EPIC simulations

* **_hrvCult** : run on cultivars, AFTER EPIC simulations
* **_hrvCrop** : run on crop, AFTER EPIC simulations


## R

```{r echo = F}
rpath <- "C:/Users/krizovak/Documents/__EPIC__/R/__epicIIASAcz/"
```

Folder for storing R scripts:

> `r rpath`

```{r echo = F}
list.files(path = "C:/Users/krizovak/Documents/__EPIC__/R/__epicIIASAcz/", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

```


## RMD

```{r echo = F}
rmdpath <- "C:/Users/krizovak/Documents/__EPIC__/R/markdown/__epicRMD/"
```

Folder for storing R scripts:

> `r rmdpath`


```{r echo = F}
list.files(paste0(rmdpath), pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

```


## GIT

R and RMD scripts are stored on [GITHUB](https://github.com/about)

> R scripts: [__epicIIASAcz](https://github.com/krizovakk/__epicIIASAcz)
 
> RMD scripts: [__epicRMD](https://github.com/krizovakk/__epicRMD)

\newpage

# SIMULATION WORKFLOW

## Cultivars

### Run Cultivars

### Hrv Cultivars

## Crop

### Run Crop

### Hrv Crop

\newpage

# VALIDATION

