---
title: "EPIC run Cultivars"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

\newpage 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(8, 4))

# install.packages("tidyverse", dependencies = T)
# install.packages("gdata")
require(tidyverse)
require(gdata) # write.fwf

```

# INITIAL SETUP

## paths 

```{r echo = T}
path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/v3_czsk/" 
path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_cultivarRESULTS/" 
```

## time period

```{r echo = T}

period <- 1989:2019 
```

## crop params

```{r}

# crop <- "ALFA"
crop <- "BARL"
# crop <- "CSIL"
# crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
# crop <- "WWHT"

# crop ID + seasonality

if(crop == "ALFA"){
  cropid <- 31 
  seas <- "OTH"
} else if (crop == "BARL"){
  cropid <- 14
  seas <- "SPG"
} else if (crop == "CSIL"){
  cropid <- 29
  seas <- "SPG"
} else if (crop == "CORN"){
  cropid <- 2
  seas <- "SPG"
} else if (crop == "OATS"){
  cropid <- 16
  seas <- "SPG"
} else if (crop == "FPEA"){
  cropid <- 26
  seas <- "SPG"
} else if (crop == "POTA"){
  cropid <- 51
  seas <- "SPG"
} else if (crop == "RAPE"){
  cropid <- 122
  seas <- "WIN"
} else if (crop == "RYE") {
  cropid <- 19
  seas <- "WIN"
} else if (crop == "SGBT"){
  cropid <- 62
  seas <- "SPG"
} else if (crop == "SUNF"){
  cropid <- 7
  seas <- "SPG"
} else if (crop == "SOYB"){
  cropid <- 1
  seas <- "SPG"
} else if (crop == "WWHT"){
  cropid <- 10
  seas <- "WIN"
} else {
  print("ZEROO")
}

# basal and optimal temperature 

if(crop == "ALFA"){
  top <- 25 
  tbs <- 1 
} else if (crop %in% c("BARL", "OATS", "WWHT")){
  top <- 15 
  tbs <- 0 
} else if (crop == "CSIL"){
  top <- 25 
  tbs <- 10 
} else if (crop == "CORN"){
  top <- 22 
  tbs <- 8
} else if (crop == "FPEA"){
  top <- 15 
  tbs <- 1
} else if (crop == "POTA"){
  top <- 17 
  tbs <- 7
} else if (crop == "RAPE"){
  top <- 13.5 
  tbs <- 0
} else if (crop == "RYE"){
  top <- 12.5 
  tbs <- 0
} else if (crop == "SGBT"){
  top <- 22
  tbs <- 4
} else if (crop %in% c("SOYB", "SUNF")){
  top <- 25
  tbs <- 10
} else {
  print("ZEROO")
}

```
* crop: `r crop`

* crop ID: `r cropid`

* seasonality: `r seas`

* basal temperature: `r tbs`

* optimal temperature: `r top`

# CROP CALENDAR

> **`r crop`_crop_cal**

contains information about 

* crop and cropid

* planting and harvest days for specific cultivars (also julian)

file necessary for:

* ?

```{r}

# *** READ *** READ *** READ ** READ ***
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")
jul_cal <- read.table(paste0(path_tab, "jul_cal.csv"), header = TRUE, sep = ";") # potrebujeme ho?
# *** READ *** READ *** READ ** READ ***


crop_cal <- cultivars %>%
  select(PLN_DAY, PLN_MON, PLN_JUL, HRV_DAY, HRV_MON, HRV_JUL) %>%
  # mutate(CROPID = rep(c(cropid), times = 30)) %>%
  mutate(CROPID = rep(c(cropid), times = nrow(cultivars))) %>%
  mutate(CROP = rep(c(crop), times = nrow(cultivars)))


# *** WR *** WR *** WR ** WR ***
write.table(crop_cal, file = paste0(path_out, crop, "/", crop, "_crop_cal.csv"), row.names=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***

print(crop_cal)

```

# CALCULATING PHU FROM DLY FILES

calculates optimal PHU (potential heat units) for each cultivar

required parameters: **tbs** and **top**


```{r}

# czsk dly

# *** READ *** READ *** READ ** READ ***
wsnames <- list.files(path_met, pattern="*.dly")  # Identify file names # all dly files in weather folder
czsk_grid <- read.table(paste0(path_tab, "czsk_GRID.csv"), header = TRUE, sep = ",") %>% 
  mutate(dly = paste0(GRID, ".dly")) # selected grids for CZSK without overlaps, n=1427
# *** READ *** READ *** READ ** READ ***

df <- as.data.frame(wsnames)
czsk_merge <- merge(czsk_grid, df, by.x = "dly", by.y = "wsnames", all = T) 
getrid <- czsk_merge %>% 
  filter(is.na(GRID))
chosen <- merge(czsk_grid, df, by.x = "dly", by.y = "wsnames")
chosen_dly <- merge(czsk_grid, df, by.x = "dly", by.y = "wsnames") %>% 
  select(dly)

chosen_vec <- as.vector(chosen_dly) %>% 
  unlist(use.names=FALSE)

# batch processing dly

# wsnames <- list.files(path_met, pattern="*.dly")  # Identify file names
a_cols <- c("year", "month", "day", "srad", "tmax", "tmin", "prcp", "rhum", "wind")

for(i in 1:length(chosen_vec)) {  # FUNKCNI; 'chosen_vec' = CZSK × 'wsnames' = CZ
  a <- read.table(paste0(path_met, wsnames[i])) # reads the DLY file
  names(a) <- a_cols  # rename the columns
  a$month <- sprintf("%02d", as.numeric(a$month)) # month in format 01
  a$day <- sprintf("%02d", as.numeric(a$day)) # day in format 01
  a$datefull <- paste(a$year, a$month, a$day, sep = "-")
  a$datefull <- as.Date(a$datefull, format=c("%Y-%m-%d")) # creates full date
  # a$datefull <- format(a$datefull, format= "%Y-%m-%d")
  # ab <- a %>% filter(year %in% c(1995:2017)) %>% 
  ab <- a %>% filter(year %in% period) %>% # zkousim zadavani time period externe, kdyztak zadat rucne
    mutate(tavg = (tmax+tmin)/2) %>% # average temperature required for PHU calculation
    group_by(year) %>%  # https://stackoverflow.com/questions/12925063/numbering-rows-within-groups-in-a-data-frame
    mutate(julday = seq_along(prcp)) %>%
    mutate(phu = case_when(tavg <= tbs ~ 0,
                           (tavg > tbs)&(tavg < top) ~ tavg,
                           tavg >= top ~ top)) %>%
    mutate(phusum = cumsum(phu))
  ac <- ab %>%
    filter(julday %in% crop_cal$HRV_JUL) %>%
    group_by(julday)
  ac$julday <- as.factor(ac$julday)
  ad <- aggregate(ac[, 14], list(ac$julday), mean) # aggregates collumn 14 (==phusum) and calculates mean value for every julday
  ae <- merge(cultivars, ad, by.x = "HRV_JUL", by.y = "Group.1") # adds phusum value into cultivars list
  af <- ae[, c("runid","PLN_JUL","HRV_JUL","LVP","sow_dat","PLN_MON","PLN_DAY",
               "hrv_dat","HRV_MON","HRV_DAY","phusum")] # reorganize the column order
  af$source <- paste0(wsnames[i]) # adds column with the DLY name
  dir.create (paste0(path_out, crop, "/phusum"), showWarnings = FALSE) # show warnings F -> folder exists, but it does not interfere with the following outcomes (https://stackoverflow.com/questions/4216753/check-existence-of-directory-and-create-if-doesnt-exist)
  write.table(af, file = paste0(path_out, crop, "/phusum/", wsnames[i], ".csv"), sep = ",", row.names = F)
}

rm(a)
rm(ab)
rm(ac)
rm(ad)
rm(ae)
rm(af)
# rm(cultivars)

# combine phu files

# *** READ *** READ *** READ ** READ ***
phusumA <- list.files(path = paste0(path_out, crop, "/phusum/"),  # Identify all CSV files
                   pattern = "*.csv", full.names = TRUE) %>%
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set
# *** READ *** READ *** READ ** READ ***


phusumA$phusum <- round((phusumA$phusum-(phusumA$phusum*0.1)), digits = 2)# lower the avg PHU by 10 %, rounds on 2 decimals
phusumA$source <- str_sub(phusumA$source,1,nchar(phusumA$source)-4)


# *** WR *** WR *** WR ** WR ***
write.table(phusumA, file = paste0(path_out, crop, "/", crop, "_phusumA.csv"), row.names=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***

```

# PHU CALENDAR

> **`r crop`_phu_cal**

```{r}

# *** READ *** READ *** READ ** READ ***
eea10_simu <- read.table(paste0(path_tab, "10km_SimU_n891.csv"), header = TRUE, sep = ",")  
phusumA <- read.table(paste0(path_out, crop, "/", crop, "_phusumA.csv"), header = TRUE, sep = ";")
# *** READ *** READ *** READ ** READ **

phu_cal0 <- merge(eea10_simu, phusumA, by.x = "GRID_NO", by.y = "source", all = T) # 891 grid * 27 cultivars (BARL) = 24057

phu_cal1 <- phu_cal0 %>% 
  mutate(CROPID = cropid) %>% 
  mutate(CROP = crop) %>% 
  rename("PHU" = phusum) %>% 
  rename("scenario" = runid) %>% 
  select(SimUID, scenario, GRID_NO, KLIMREG, CROPID, CROP, PLN_JUL, HRV_JUL, LVP, PHU) %>% 
  group_by(GRID_NO, scenario) %>% 
  dplyr::mutate(runid = cur_group_id())


# *** WR *** WR *** WR ** WR ***
write.table(phu_cal1, paste0(path_out, crop, "/", crop, "_phu_cal.csv"), row.names = F, quote = F, sep = ";")
# *** WR *** WR *** WR ** WR ***

phu_cal_runid <- phu_cal1 %>% 
  select(SimUID, GRID_NO, scenario, runid, KLIMREG) # link of runid, scenario, GRID and original SimU


# *** WR *** WR *** WR ** WR ***
write.table(phu_cal_runid, paste0(path_out, crop, "/", crop, "_phu_cal_runid.csv"), row.names = F, quote = F, sep = ";")
# *** WR *** WR *** WR ** WR ***

rm(phu_cal0)
rm(phu_cal1)
rm(phusumA)

```

# EPIC INPUT FILES

```{r echo=T}

# create directories
dir.create (paste0(path_out, crop, "/epicrun"), showWarnings = FALSE)
dir.create (paste0(path_out, crop, "/OPSC"), showWarnings = FALSE)
dir.create (paste0(path_out, crop, "/PARM"), showWarnings = FALSE)
dir.create (paste0(path_out, crop, "/_simulated"), showWarnings = FALSE)
```


## 2 PRINT

files that needs to be uploaded to MS Access projects and print in Visual Basic

### OPC

> **`r crop`_OPSC_cultivars_2print.txt** 

operation schedules

necessary table: **OPSC_Param_SVK13.txt**

```{r}

# crop_parm file has different crop abbrevs -> adjust:

if(crop == "ALFA"){
  cropp <- "ALF"
} else if (crop == "BARL"){
  cropp <- "BAR"
} else if (crop == "CSIL"){
  cropp <- "MAI"
} else if (crop == "CORN"){
  cropp <- "MAI" # ???????????????????????????????????????
} else if (crop == "OATS"){
  cropp <- "OAT"
} else if (crop == "FPEA"){
  cropp <- "PEA"
} else if (crop == "POTA"){
  cropp <- "POT"
} else if (crop == "RAPE"){
  cropp <- "RAP"
} else if (crop == "RYE") {
  cropp <- "RYE"
} else if (crop == "SGBT"){
  cropp <- "SGB"
} else if (crop == "SUNF"){
  cropp <- "SNF"
} else if (crop == "SOYB"){
  cropp <- "SOY"
} else if (crop == "WWHT"){
  cropp <- "WHE"
} else {
  print("ZEROO")
}


# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal_grid.csv"), header = TRUE, sep = ";")
crop_cal <- read.table(paste0(path_out, crop, "/", crop, "_crop_cal.csv"), header = TRUE, sep = ";")
crop_parm <- read.table(paste0(path_tab, "OPSC_Param_SVK13.txt"), header = TRUE, sep = ";")  # all crops by default
# *** READ *** READ *** READ ** READ ***

crop_parm <- crop_parm %>%
  filter(CROP == cropp)  %>%   # filter parameters for current crop only
  select(-CROP)

# combine tables for OPSC / step by step according to ms access


opsc1 <- merge(phu_cal, crop_cal, by = c("CROP", "CROPID", "PLN_JUL", "HRV_JUL")) 
opsc2 <- merge(opsc1, crop_parm, by = c("CROPID")) # 24057 (grid*cultivars) * 6 (operations) = 144342

opsc3 <- opsc2 %>% # 8640
  mutate(OPMONTH = case_when(OPERATION %in% c("HARV", "KILL") ~ HRV_MON,
                             OPERATION %in% c("FRTK", "FRTP", "TILL", "SOW") ~ PLN_MON)) %>%
  mutate(OPDAY = case_when(OPERATION %in% c("HARV", "KILL") ~ HRV_DAY,
                           OPERATION %in% c("FRTK", "FRTP", "TILL", "SOW") ~ PLN_DAY)) %>%
  mutate(Seq = case_when(seas == "SPG" ~ Seq1, 
                         seas == "WIN" ~ Seq2))  %>% # sequence of operations differ for SPG and WIN crops
  mutate(PARAMETER2 = case_when(OPERATION == "SOW" ~ round(PHU, 0),
                                OPERATION %in% c("FRTK", "FRTP") ~ 25, TRUE ~ 0)) %>%  # https://www.sharpsightlabs.com/blog/case-when-r/
  select(runid, scenario, GRID_NO,	KLIMREG,	CROPID,	CROP,	CropSpec,	OPERATION,	LUN, Year, OPMONTH,	OPDAY,
         Seq,	IHC,	TYPE,	PARAMETER1,	PARAMETER2,	PARAMETER3,	PARAMETER4,
         PARAMETER5,	PARAMETER6,	PARAMETER7) %>% 
  arrange(GRID_NO, scenario, Seq) 
  # group_by(GRID_NO, scenario) %>% 
  # dplyr::mutate(SimUId = cur_group_id()) 

# *** WR *** WR *** WR ** WR ***
write.table(opsc3, file = paste0(path_out, crop, "/", crop, "_OPSC_cultivars_2print.txt"),
            row.names=FALSE, quote=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***

rm(opsc1)
rm(opsc2)
rm(opsc3)
rm(crop_cal)
rm(crop_parm)


```

### EPICRUN

> **`r crop`_epicrun_cultivars_2print.txt** 

EPICRUN for initial calibrations runs works with only 1 SIT and SOL file for all grids

* **SIT**  

    + CZ: 119
    + SK: ?

* **SOL** 

    + CZ: 10
    + SK: 7 ?
    
* **OPC** created for each 'runid' (runid 167 = 167.opc)

* **DLY** created for each 'runid' (runid 167 = 167.dly) / same for WP1

* **WINDID** set as 1 for each 'runid'


    
```{r}

# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal_grid.csv"), header = TRUE, sep = ";")
# *** READ *** READ *** READ ** READ ***

# modify table to epicrun

epicrun0 <- phu_cal %>%
  select(runid, GRID_NO) %>%
  mutate(SIT = 119) %>%
  mutate(SOL = 10) %>%
  mutate(OPC = runid) %>%
  mutate(WP1 = GRID_NO) %>%
  mutate(DLY = GRID_NO) %>%
  mutate(WINDID = 1) %>%
  distinct()

# *** WR *** WR *** WR ** WR ***
write.table(epicrun0, file = paste0(path_out, crop, "/", crop, "_epicrun_cultivars_2print.txt"),
                               row.names=FALSE, quote=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***

rm(epicrun0)

```


### PARMFILES

> **`r crop`_PARM_cultivars_2print.txt** 

?

necessary table: **CZ_PARM0810tab_v0.txt**

```{r}

# *** READ *** READ *** READ ** READ ***
parm0 <- read.table(paste0(path_tab, "CZ_PARM0810tab_v0.txt"), header = TRUE, sep = ";")
sel_simu <- read.table(paste0(path_tab, "10km_SimU_n891.csv"), header = TRUE, sep = ",")
# *** READ *** READ *** READ ** READ ***

parm1 <- parm0 %>%
  filter(SimUID %in% sel_simu$SimUID)

parm2 <- merge(parm1, phu_cal_runid, by.x = "SimUID", by.y = "SimUID", all.y = T)

# *** WR *** WR *** WR ** WR ***
write.table(parm2, file = paste0(path_out, crop, "/", crop, "_PARM_cultivars_2print.txt"),
            row.names=FALSE, quote=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***



```


## 4 EPIC

files ready to be used by EPIC


### OPSCCOM

**OPSCCOM.dat**

?

```{r}

# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal_grid.csv"), header = TRUE, sep = ";")
# *** READ *** READ *** READ ** READ ***
 

opsccom <- phu_cal %>%
  select(runid) %>%
  # rename("SimUID" = GRID_NO) %>%
  # select(SimUID) %>%
  mutate(file = paste(runid,".opc", sep = "")) %>%
  distinct()


# *** WR *** WR *** WR ** WR ***
write.fwf(opsccom, paste0(path_out, crop, "/OPSCCOM.dat"),
          rownames = FALSE, colnames = FALSE,
          formatInfo = TRUE, sep = "  ")
# *** WR *** WR *** WR ** WR ***

```


### SITECOM

**SITECOM.dat**

?

```{r}
sitecom <- phu_cal %>% 
  select(runid) %>% 
  mutate(file = "119.sit") %>%
  distinct()

# *** WR *** WR *** WR ** WR ***
write.fwf(sitecom,paste0(path_out, crop, "/SITECOM.dat"),
          rownames = FALSE, colnames = FALSE,
          formatInfo = TRUE, sep = "  ")
# *** WR *** WR *** WR ** WR ***

```


### SOILCOM

**SOILCOM.dat**

?

```{r}
soilcom <- phu_cal %>%
  select(runid) %>% 
  mutate(file = "10.sol") %>% # 10 == chernozem ; 210 == sandy soil
  distinct()

# *** WR *** WR *** WR ** WR ***
write.fwf(soilcom, paste0(path_out, crop, "/SOILCOM.dat"),
          rownames = FALSE, colnames = FALSE,
          formatInfo = TRUE, sep = "  ")
# *** WR *** WR *** WR ** WR ***

rm(opsccom)
rm(sitecom)
rm(soilcom)
# rm(phu_cal_grid)

```



