---
title: "EPIC harvest Cultivars"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: html_document
---

```{r eval=F, echo = F}
title: "EPIC harvest Cultivars"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
```


\newpage 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(8, 4))

# install.packages("tidyverse", dependencies = T)
# install.packages("gdata")
require(tidyverse)
require(gdata) # write.fwf
library(sf)
library(sp)
library(rgdal)
require(reshape2)
require(ggpubr)
library(knitr)

```

# INITIAL SETUP

## paths 

```{r echo = T}
path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/v3_czsk/" 
path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_cultivarRESULTS/" 

```

## time period

```{r echo = T}

period <- 1989:2019 
```

## crop params

```{r}

# crop <- "ALFA"
# crop <- "BARL"
# crop <- "CSIL"
# crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
crop <- "WWHT"


# crop ID + seasonality

if(crop == "ALFA"){
    cropid <- 31 
    cropname <- "alfalfa"
    seas <- "OTH"
  } else if (crop == "BARL"){
    cropid <- 14
    cropname <- "spring barley"
    seas <- "SPG"
  } else if (crop == "CSIL"){
    cropid <- 29
    cropname <- "corn silage"
    seas <- "SPG"
  } else if (crop == "CORN"){
    cropid <- 2
    cropname <- "corn"
    seas <- "SPG"
  } else if (crop == "OATS"){
    cropid <- 16
    cropname <- "oat"
    seas <- "SPG"
  } else if (crop == "FPEA"){
    cropid <- 26
    cropname <- "field peas"
    seas <- "SPG"
  } else if (crop == "POTA"){
    cropid <- 51
    cropname <- "potatoes"
    seas <- "SPG"
  } else if (crop == "RAPE"){
    cropid <- 122
    cropname <- "winter rapeseed"
    seas <- "WIN"
  } else if (crop == "RYE") {
    cropid <- 19
    cropname <- "rye"
    seas <- "WIN"
  } else if (crop == "SGBT"){
    cropid <- 62
    cropname <- "sugarbeet"
    seas <- "SPG"
  } else if (crop == "SUNF"){
    cropid <- 7
    cropname <- "sunflower"
    seas <- "SPG"
  } else if (crop == "SOYB"){
    cropid <- 1
    cropname <- "soybean"
    seas <- "SPG"
  } else if (crop == "WWHT"){
    cropid <- 10
    cropname <- "winter wheat"
    seas <- "WIN"
  } else {
    print("ZEROO")
}


# WCY parameter (fraction water in yield ) WCY = 0.12 -> yield + wcy -> 1.12

# ??? RAPE ???

wcy <- case_when(crop %in% c("ALFA", "BARL", "FPEA", "RYE", "WWHT") ~ 1.12,
                 crop %in% c("CSIL", "CORN") ~ 1.15, 
                 crop %in% c("OATS") ~ 1.10, 
                 crop %in% c("POTA") ~ 1.8, 
                 crop %in% c("SGBT") ~ 1.84, 
                 crop %in% c("SUNF") ~ 1.06, 
                 crop %in% c("SOYB") ~ 1.13) 

```

\newpage 

# HARVEST OUTPUT FILES

## ACM

output file stored in 'EPIC0810'

?

```{r eval=FALSE}

# load ACM files without 11 lines of header and save it as csv

acmnames <- list.files(path_epic, pattern= "\\.ACM$")  # Identify file names
acmnamesWO <- tools::file_path_sans_ext(acmnames) # remove the extension '.ACM'

for(i in 1:length(acmnames)) {
  a <- read.table(paste0(path_epic, acmnames[i]), header = FALSE, skip = 11)
  a$source <- paste0(acmnamesWO[i])
  dir.create (paste0(path_out, crop, "/_simulated/ACM"), showWarnings = FALSE)
  write.csv(a, file = paste0(path_out, crop, "/_simulated/ACM/", acmnamesWO[i], ".csv"))
}


# read csv and bind them into one single file


acmcomb <- list.files(path = paste0(path_out, crop, "/_simulated/ACM"),     # https://statisticsglobe.com/merge-csv-files-in-rhttps://statisticsglobe.com/merge-csv-files-in-r
                      pattern = "*.csv", full.names = TRUE) %>%  # Identify all csv files in folder
  lapply(read_csv) %>%                                            # Store all files in list
  bind_rows                                                       # Combine data sets into one data set


# rename header

col_names_acm <- c("X", "YR",  "RT", "PRCP", "PET", "ET ", "Q", "SSF", "PRK", "CVF", "MUSS", "YW", "GMN", "NMN", "NFIX", "NITR", "AVOL",
                   "DN", "YON", "QNO3", "SSFN", "PRKN", "MNP", "YP", "QAP", "PRKP", "LIME", "OCPD", "TOC", "APBC", "TAP", "TNO3", "SimUID")
names(acmcomb) <- col_names_acm


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acmcomb, file = paste0(path_out, "_simulated/", currentDate, "_", crop, "_acm.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```

## ACY

output file stored in 'EPIC0810'

?

```{r eval=F}

# load ACY files without 11 lines of header and save it as csv

acynames <- list.files(path_in, pattern= "\\.ACY$")  # Identify file names
acynamesWO <- tools::file_path_sans_ext(acynames) # remove the extension '.ACM'


for(i in 1:length(acynames)) {
  a <- read.table(paste0(path_epic, acynames[i]), header = FALSE, skip = 11)
  a$source <- paste0(acynamesWO[i])
  dir.create (paste0(path_out, crop, "/_simulated/ACY"), showWarnings = FALSE)
  write.csv(a, file = paste0(path_out, crop, "/_simulated/ACY/", acynamesWO[i], ".csv"))
}


# read csv and bind them into one single file


acycomb <- list.files(path = paste0(path_out, crop, "/_simulated/ACY"),     # https://statisticsglobe.com/merge-csv-files-in-rhttps://statisticsglobe.com/merge-csv-files-in-r
                      pattern = "*.csv", full.names = TRUE) %>%  # Identify all csv files in folder
  lapply(read_csv) %>%                                            # Store all files in list
  bind_rows                                                       # Combine data sets into one data set


# rename header

col_names_acy <- c("X", "YR",  "RT", "CPNM", "YLDG", "YLDF ", "BIOM", "YLN", "YLP", "FTN", "FTP", "IRGA", "IRDL",
                   "WUEF", "GSET", "CAW", "CRF", "CQV", "COST", "COOP", "RYLG", "RYLF", "PSTF", "WS", "NS", "PS",
                   "KS", "TS", "AS", "SS", "PPOP", "IPLD", "IGMD", "IHVD", "SimUID")
names(acycomb) <- col_names_acy


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acycomb, file = paste0(path_out, "_simulated/", currentDate, "_", crop, "_acy.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```

## OUTPUT TABLE

```{r}

# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal.csv"), header = TRUE, sep = ";")
jul_cal <- read.table(paste0(path_tab, "jul_cal.csv"), header = TRUE, sep = ";")
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")


acm <- read.table(paste0(path_out, crop, "/_simulated/ACM_msacc.txt"), header = T, sep = ";")
acy <- read.table(paste0(path_out, crop, "/_simulated/ACY_msacc.txt"), header = T, sep = ";")

# OR ?
  
# if (seas == "SPG"){
#   acy <- read.table(paste0(path_in, "ACY_BAR_2309.txt"), header = T, sep = ";") %>% 
#     filter(YR %in% c(1995:2017))
# }  else if (seas == "WIN"){
#   acy <- read.table(paste0(path_in,  "ACY_BAR_2309.txt"), header = T, sep = ";") %>% 
#   filter(YR %in% c(1995:2017)) %>% 
#   filter(IHVD != 0)
# } else {
#   print("ZEROO")
# }

# *** READ *** READ *** READ ** READ ***


# merge ACM and ACY; apply WCY parameter

outtab0 <- merge(acm, acy, all = T) 
outtab <- merge(outtab0, phu_cal, by.x = "runid", by.y = "runid") # join ACM and ACY with SCENARIO
outtab$YLDG <- (outtab$YLDG*wcy) # WCY parameter / fraction water in yield 
# outtab <- outtab %>%
#   mutate(PO = case_when(KLIMREG == 0 ~ "K",
#                         KLIMREG %in% c(1:3) ~ "R",
#                         KLIMREG %in% c(4:5) ~ "C",
#                         KLIMREG %in% c(6:7) ~ "B",
#                         KLIMREG %in% c(8:9) ~ "H"))

rm(acm)
rm(acy)
rm(phu_cal)
rm(outtab0)


# outtab == output tables; YLDG corrected with WCY parameter

```

\newpage 

# CULTIVARS REVIEW

## CULTIVARS

```{r results='asis'}

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")
   # cat('\n')
   # cat("This is a heading for ", croplist[i] , "\n")
   # kable(cultivars, caption = paste0("Cultivars of ", cropname))
   # cat('\n')
   tab <- kable(cultivars, caption = paste0("Cultivars of ", cropname))
   print(tab)

```

## MAP YIELD FOR ALL SCENARIOS

```{r eval=F, results='asis'}

out_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, PRCP, PET, TS) %>% 
  group_by(runid) %>% 
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPRCP = mean(PRCP), 
            avgPET = mean(PET), avgTS = mean(TS)) %>% 
  distinct()

scen_list <- levels(as.factor(out_scen$scenario))
# print(scen_list)

for(i in 1:length(scen_list)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- scen_list[i]
  filt_scen <- filter(out_scen, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
    geom_sf()+
    ggtitle(paste0("Average yield of ", cropname, " in 1989-2019 / scenario: ", scene )) + 
    scale_fill_gradient("[t/ha]", 
    low = "yellow",
    high = "darkgreen",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill", 
    limits = c(1,7))+ # !!!!!!!!!!!!!!!! adjust
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_yld)
}

```

## DESCRIPTIVE STATISTICS

descriptive statistics for each grid
calculated from all `r nrow(cultivars)` cultivars

```{r eval=FALSE}
destat <- outtab %>% 
select(runid, YR, scenario, GRID_NO, YLDG) %>% 
  group_by(GRID_NO) %>% 
  summarise(GRID_NO, minYLD = min(YLDG), maxYLD = max(YLDG),
            avgYLD = mean(YLDG), sdYLD = sd(YLDG)) %>% 
  mutate(ranYLD = maxYLD-minYLD) %>% 
  distinct()

# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)

desshp <-sp::merge(destat, gridmap, by.x = "GRID_NO", by.y = "GRID")

# mean

ggplot(desshp, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Mean simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                     high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# range

ggplot(desshp, aes(geometry = geometry, fill= ranYLD))+
  geom_sf()+
  ggtitle(paste0("Range of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# sd

ggplot(desshp, aes(geometry = geometry, fill= sdYLD))+
  geom_sf()+
  ggtitle(paste0("Standard deviation of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "red",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

```

\newpage 

# SCENARIO SELCTION

criteria: 

* lowest IHVD shift

* lowest IPLD shift

* IPLD - IGMD < 21 days 

* highest yield

working DF: **dat_shft**


### IPLD + IGMD

### IHVD + IPLD

IPLD and IHVD dates shifted compared to the dates given by cultivar setup

calculate the shift

sum IPLD and IHVD shift

picks scenario with the lowest number of days

**selected:**


```{r preparing DF with calculated shifts, message=FALSE}

# merge output table with designed cultivar

outtab <- if(crop == "WWHT"){
  filter(outtab, IHVD != 0)
} else {outtab <- outtab}


hvd_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, IPLD, IGMD, IHVD) %>% 
  merge(cultivars, by.x = "scenario", by.y = "runid") %>% 
  mutate(gIPLD = paste0(YR, sprintf("%02d", PLN_MON), sprintf("%02d", PLN_DAY))) %>% # given IPLD
  mutate(gIHVD = paste0(YR, sprintf("%02d", HRV_MON), sprintf("%02d", HRV_DAY))) # given IHVD
  

# formatting date

hvd_scen$IPLD <- as.Date(as.character(hvd_scen$IPLD), format = "%Y%m%d")
hvd_scen$IGMD <- as.Date(as.character(hvd_scen$IGMD), format = "%Y%m%d")
hvd_scen$IHVD <- as.Date(as.character(hvd_scen$IHVD), format = "%Y%m%d")

hvd_scen$gIPLD <- as.Date(hvd_scen$gIPLD, format = "%Y%m%d")
hvd_scen$gIHVD <- as.Date(hvd_scen$gIHVD, format = "%Y%m%d")

# difference of IPLD and IHVD in days

hvd_scen$p_diff <- as.numeric(difftime(hvd_scen$gIPLD, hvd_scen$IPLD, units = "days"))
hvd_scen$h_diff <- as.numeric(difftime(hvd_scen$gIHVD, hvd_scen$IHVD, units = "days"))

# difference of IPLD and IGMD

hvd_scen$g_diff <- as.numeric(difftime(hvd_scen$IGMD, hvd_scen$gIPLD, units = "days"))

# avg date shift for scenario

dat_shft <- hvd_scen %>% 
  group_by(runid) %>%
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPshft = mean(p_diff), avgHshft = mean(h_diff)) %>% # avgPRCP = mean(PRCP), avgPET = mean(PET), avgTS = mean(TS)
  distinct() %>% 
  mutate(H = abs(avgHshft)) %>% 
  mutate(P = abs(avgPshft)) %>% 
  mutate(HPsum = H+P) # sum of P and H days
  
# pick scenario

selHP <- dat_shft %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(HPsum)) 
 
# filter(dat_shft, GRID_NO == 497)
# filter(pick, GRID_NO == 497) # only check

selHP$scenario <- as.factor(selHP$scenario)
summary(selHP$scenario)
```
```{r results='asis'}
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
HPcult <- selHP$scenario

HPsel <- cultivars %>% 
  filter(runid %in% HPcult)
tab <- kable(HPsel, caption = paste0("Selected cultivars of ", cropname))
print(tab)
```


```{r}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selHP, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname)) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)

```

### YIELD + IHVD

scenario with the lowest IHVD shift and highest yield

**selected:**

```{r}
selHY <- dat_shft %>% 
  group_by(GRID_NO) %>%
  filter(H == min(H)) %>%
  filter(avgYLD == max(avgYLD))
  # slice(which.min(HPsum)) 
 
# filter(dat_shft, GRID_NO == 497)
# filter(pick, GRID_NO == 497) # only check

selHY$scenario <- as.factor(selHY$scenario)
summary(selHY$scenario)

```
```{r results='asis'}
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
HYcult <- selHY$scenario

HYsel <- cultivars %>% 
  filter(runid %in% HYcult)
tab <- kable(HYsel, caption = paste0("Selected cultivars of ", cropname))
print(tab)
```

```{r}
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selHY, gridmap, by.x = "GRID_NO", by.y = "GRID")
ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname)) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)

```

\newpage

# FINAL SELECT

```{r}

out_scen <- outtab %>%  # yearly average values for each runid
  select(runid, YR, scenario, GRID_NO, YLDG, PRCP, PET, TS) %>% 
  group_by(runid) %>% 
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPRCP = mean(PRCP), 
            avgPET = mean(PET), avgTS = mean(TS)) %>% 
  distinct()

pick_scen <- out_scen %>% 
  group_by(GRID_NO) %>% 
  filter(avgYLD == max(avgYLD)) # ?!?!?!?!?!?!?!?!?!?!


# *** WR *** WR *** WR ** WR ***
write.table(pick_scen, file = paste0(path_out, crop, "/", crop, "_selectedScen.csv"), row.names=FALSE, sep = ";")
# *** WR *** WR *** WR ** WR ***

```
\newpage

# RENDER

```{r}

# install.packages("rmarkdown")
library(rmarkdown)
render("EPIC_hrvCult.Rmd", output_file = paste0("c:/Users/krizovak/Documents/__EPIC__/R/markdown/reports/", crop, "_hrvCultReport"))

```

