---
title: "EPIC harvest Cultivars - parallelized"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

\newpage 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(8, 4))

# install.packages("tidyverse", dependencies = T)
# install.packages("gdata")
require(tidyverse)
require(gdata) # write.fwf
library(sf)
library(sp)
library(rgdal)
require(reshape2)
require(ggpubr)
library(knitr)

```

# INITIAL SETUP

## paths 

```{r echo = T}

path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/v3_czsk/" 
path_epic <- "c:/Users/krizovak/Documents/__EPIC__/EPIC_CS_v4_Aug2022/" 

path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_cultivarRESULTS/" 

```

## time period

```{r echo = T}
period <- 1989:2019 
```



## crop params

```{r}

# crop <- "ALFA"
crop <- "BARL"
# crop <- "CSIL"
# crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
# crop <- "WWHT"


# crop ID + seasonality

if(crop == "ALFA"){
    cropid <- 31 
    cropname <- "alfalfa"
    seas <- "OTH"
  } else if (crop == "BARL"){
    cropid <- 14
    cropname <- "spring barley"
    seas <- "SPG"
  } else if (crop == "CSIL"){
    cropid <- 29
    cropname <- "corn silage"
    seas <- "SPG"
  } else if (crop == "CORN"){
    cropid <- 2
    cropname <- "corn"
    seas <- "SPG"
  } else if (crop == "OATS"){
    cropid <- 16
    cropname <- "oat"
    seas <- "SPG"
  } else if (crop == "FPEA"){
    cropid <- 26
    cropname <- "field peas"
    seas <- "SPG"
  } else if (crop == "POTA"){
    cropid <- 51
    cropname <- "potatoes"
    seas <- "SPG"
  } else if (crop == "RAPE"){
    cropid <- 122
    cropname <- "winter rapeseed"
    seas <- "WIN"
  } else if (crop == "RYE") {
    cropid <- 19
    cropname <- "rye"
    seas <- "WIN"
  } else if (crop == "SGBT"){
    cropid <- 62
    cropname <- "sugarbeet"
    seas <- "SPG"
  } else if (crop == "SUNF"){
    cropid <- 7
    cropname <- "sunflower"
    seas <- "SPG"
  } else if (crop == "SOYB"){
    cropid <- 1
    cropname <- "soybean"
    seas <- "SPG"
  } else if (crop == "WWHT"){
    cropid <- 10
    cropname <- "winter wheat"
    seas <- "WIN"
  } else {
    print("ZEROO")
}


# WCY parameter (fraction water in yield ) WCY = 0.12 -> yield + wcy -> 1.12

# ??? RAPE ???

wcy <- case_when(crop %in% c("ALFA", "BARL", "FPEA", "RYE", "WWHT") ~ 1.12,
                 crop %in% c("CSIL", "CORN") ~ 1.15, 
                 crop %in% c("OATS") ~ 1.10, 
                 crop %in% c("POTA") ~ 1.8, 
                 crop %in% c("SGBT") ~ 1.84, 
                 crop %in% c("SUNF") ~ 1.06, 
                 crop %in% c("SOYB") ~ 1.13) 

epic_parall <- c(1:8)
```
* crop: `r crop`

* crop ID: `r cropid`

* crop name: `r cropname`

* seasonality: `r seas`

* WCY parameter: `r wcy`

\newpage 

# HARVEST OUTPUT FILES (in progress)

Steps necessary to take AFTER simulation

## COPY AND PASTE ACM AND ACY

EPIC output files are stored in **EPIC_CS_X/EPIC0810** folder

Backup files:

* create a folder '_outs' in cultivar results folder

* create a subfolder 'crop_outs_currentDate' in '_outs' folder

* copy all files in both newly created folders, so that: 

  + there is a backup in date-named folder
  
  + there are always the latest ACM and ACY files to be further worked with

```{r COPY ACM AND ACY}

# batch

for(i in 1:length(epic_parall)) {
  currentDate <- Sys.Date()
  dir.create(paste0(path_out, crop, "/_outs/outs_", currentDate), showWarnings = FALSE) #showWarnings = FALSE -> folder is not overwritten, files copied into the firstly created one
  path_source <- paste0(path_epic,"EPIC_CS_", i, "/EPIC0810/")
  Louts <- list.files(path_source, pattern = ".ACM|.ACY") # pattern either ACM or ACY (only AC was not enough because of WORKSPACE file)
  newDir <- paste0(path_out, crop, "/_outs/outs_", currentDate, "/")
  newDir2 <- paste0(path_out, crop, "/_outs/")
  file.copy(from = paste0(path_source, Louts),   # Output files backup in folder with date
          to = paste0(newDir, Louts))
  file.copy(from = paste0(path_source, Louts),   # Latest ouptut files in '_outs' folder
          to = paste0(newDir2, Louts), overwrite = TRUE)
}

# ACM and ACY files are deleted befor a new run (EPIC_runCult.Rmd)

# # !!! FINAL !!! FINAL !!! FINAL !!!
# for(i in 1:length(epic_parall)) {
#   path_source <- paste0(path_epic,"EPIC_CS_", i, "/EPIC0810/")
#   Louts <- list.files(path_source, pattern = ".ACM|.ACY")
#   file.remove(paste0(path_source, Louts)) # ACM and ACY files removal from EPIC0810 folder
# }
# # !!! FINAL !!! FINAL !!! FINAL !!!

# single 

currentDate <- Sys.Date()
dir.create(paste0(path_out, crop, "/_outs/outs_", currentDate), showWarnings = FALSE) #showWarnings = FALSE -> folder is not overwritten, files copied into the firstly created one
path_source <- paste0(path_epic,"EPIC_CS_4/EPIC0810/")
Louts <- list.files(path_source, pattern = ".ACM|.ACY") # pattern either ACM or ACY (only AC was not enough because of WORKSPACE file)
newDir <- paste0(path_out, crop, "/_outs/outs_", currentDate, "/")
newDir2 <- paste0(path_out, crop, "/_outs/")
file.copy(from = paste0(path_source, Louts),   # Output files backup in folder with date
          to = paste0(newDir, Louts))
file.copy(from = paste0(path_source, Louts),   # Latest ouptut files in '_outs' folder
          to = paste0(newDir2, Louts), overwrite = TRUE)

# remove files and paths

rm(path_source)
rm(path_temp)
rm(Louts)
rm(newDir)
rm(newDir2)

```

## ACM HARVEST

*Annual cropman file*

Variable / Description / Units
Y = Year
RT# = Rotation number
PRCP = Precipitation mm
ET = Potential evapotranspiration mm
ET = Evapotranspiration mm
Q = Runoff mm
SSF = Subsurface flow mm
PRK = Percolation mm
CVF = MUSLE crop cover factor
MUSS = Water erosion T/ha
YW = Wind erosion T/ha
GMN = N mineralized kg/ha
NMN = Humus mineralization kg/ha
NFIX = Nitrogen fixation kg/ha
NITR = Nitrification kg/ha
AVOL = Nitrogen volatilization kg/ha
DN = Denitrification kg/ha
YON = Nitrogen loss with sediment kg/ha
QNO3 = Nitrate loss in surface runoff kg/ha
SSFN = Nitrogen in subsurface flow kg/ha
PRKN = Nitrogen loss in percolate kg/ha
MNP = Phosphorus mineralized kg/ha
YP = Phosphorus loss in sediment kg/ha
QAP = Labile phosphorus loss in runoff kg/ha
PRKP = Phosphorus loss in percolate kg/ha
LIME = Lime applied kg/ha
OCPD = Organic carbon in plow layer depth set by PARM(16) kg/ha
TOC = Organic carbon in soil profile kg/ha
APBC = Labile phosphorus content in plow layer %
TAP = Total labile p in soil profile kg/ha
TNO3 = Total nitrate in soil profile kg/ha

```{r ACM HARVEST, eval=FALSE}

# load ACM files without 11 lines of header, combine into a single df

acmnames <- list.files(paste0(path_out, crop, "/_outs/"), pattern= "\\.ACM$")  # Identify file names

acm_comb = data.frame() # empty dataframe to write ACM files in

for(i in acmnames) { # TAKES AGES !!
  a <- read.table(paste0(path_out, crop, "/_outs/", i), header = FALSE, skip = 11)
  a$source <- paste0(i)
  a$source <- str_sub(a$source,1,nchar(a$source)-4)
  df <- data.frame(a) 
  acm_comb <- rbind(acm_comb, df)
}

# rename header

col_names_acm <- c("YR",  "RT", "PRCP", "PET", "ET ", "Q", "SSF", "PRK", "CVF", "MUSS", "YW", "GMN", "NMN", "NFIX", "NITR", "AVOL",
                   "DN", "YON", "QNO3", "SSFN", "PRKN", "MNP", "YP", "QAP", "PRKP", "LIME", "OCPD", "TOC", "APBC", "TAP", "TNO3", "runid")
names(acm_comb) <- col_names_acm
# names(acm) <- col_names_acm


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acm_comb, file = paste0(path_out, crop, "/_outs/acm.csv"), row.names=FALSE)
write.csv(acm_comb, file = paste0(path_out, crop, "/_outs/outs_", currentDate,"/",
                                 currentDate, "_", crop, "_acm.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```

## ACY HARVEST

*Annual Crop Yield*

Variable / Description / Units
Y = Year
RT# = Fertilizer ID
CPNM = Crop name
YLDG = Grain yield T/ha
YLDF = Forage yield T/ha
BIOM Biomass T/ha
YLN = Nitrogen used by crop kg/ha
YLP = Phosphorus used by crop kg/ha
FTN = Nitrogen applied kg/ha
FTP = Phosphorus applied kg/ha
IRGA = Irrigation volume applied mm
IRDL = Irrigation water lost in delivery system mm
WUEF = Water use efficiency (crop yield / growing season ET) kg/mm
GSET = Growing season et (mm) mm
CAW = Crop available water (soil water at planting + growing season rainfall - runoff) mm
CRF = Growing season rainfall mm
CQV = Growing season runoff mm
COST = Cost of production $/ha
COOP = Operating cost $/ha
RYLG = Return for grain yield $/ha
RYLF = Return for forage yield $/ha
PSTF = Pest damage factor (fraction of yield remaining after pest damage
WS = Water stress days d/yr
NS = Nitrogen stress days d/yr
PS = Phosphorus stress days d/yr
KS = Potassium stress days d/yr
TS = Temperature stress days d/yr
AS = Aeration stress days d/yr
SS = Salinity stress factor
PPOP = Plant population plants/m2
IPLD = Planting date
IGMD = Germination date
IHVD = Harvest date

```{r ACY HARVEST, eval=F}

# load ACY files without 11 lines of header and a single file

acynames <- list.files(paste0(path_out, crop, "/_outs/"), pattern= "\\.ACY$")   # Identify file names

acy_comb = data.frame() # empty dataframe to write ACM files in

for(i in acynames) { # TAKES AGES !!
  a <- read.table(paste0(path_out, crop, "/_outs/", i), header = FALSE, skip = 11)
  a$source <- paste0(i)
  a$source <- str_sub(a$source,1,nchar(a$source)-4)
  df <- data.frame(a) 
  acy_comb <- rbind(acy_comb, df)
}

# rename header

col_names_acy <- c("YR",  "RT", "CPNM", "YLDG", "YLDF", "WCYD", "HI", "BIOM", "RW", 
                   "YLN", "YLP", "YLC", "FTN", "FTP", "IRGA", "IRDL", "WUEF", "GSET", 
                   "CAW", "CRF", "CQV", "COST", "COOP", "RYLG", "RYLF", "PSTF", 
                   "WS", "NS", "PS", "KS", "TS", "AS", "SS", "PPOP", 
                   "IPLD", "IGMD", "IHVD", "runid")
names(acy_comb) <- col_names_acy
names(acy) <- col_names_acy


# *** WR *** WR *** WR ** WR ***
currentDate <- Sys.Date()
write.csv(acy_comb, file = paste0(path_out, crop, "/_outs/acy.csv"), row.names=FALSE)
write.csv(acy_comb, file = paste0(path_out, crop, "/_outs/outs_", currentDate,"/",
                                 currentDate, "_", crop, "_acy.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***


rm(acm_comb)
rm(acy_comb)
```


## OUTPUT TABLE

ACM and ACY tables combined in one
Contains all important outputs of the simulation

```{r OUTPUT TABLE}

# *** READ *** READ *** READ ** READ ***
phu_cal <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal.csv"), header = TRUE, sep = ";")
# jul_cal <- read.table(paste0(path_tab, "jul_cal.csv"), header = TRUE, sep = ";")
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")

# acm <- read.table(paste0(path_out, crop, "/_outs/acm.csv"), header = T, sep = ";")
# acy <- read.table(paste0(path_out, crop, "/_outs/acy.csv"), header = T, sep = ";")

# OR ?
  
if (seas == "SPG"){
  acm <- read.table(paste0(path_out, crop, "//_outs/acm.csv"), header = T, sep = ",")
  acy <- read.table(paste0(path_out, crop, "//_outs/acy.csv"), header = T, sep = ",")
}  else if (seas == "WIN"){
  acm <- read.table(paste0(path_out, crop, "//_outs/acm.csv"), header = T, sep = ",") %>%
  filter(YR != 1989)
  acy <- read.table(paste0(path_out, crop, "//_outs/acy.csv"), header = T, sep = ",") %>%
  filter(IHVD != 0)
} else {
  print("ZEROO")
}
# *** READ *** READ *** READ ** READ ***


# merge ACM and ACY; apply WCY parameter

outtab0 <- merge(acm, acy) %>% 
  filter(YR != 1989)
outtab <- merge(outtab0, phu_cal, by.x = "runid", by.y = "runid") # join ACM and ACY with SCENARIO
outtab$YLDG <- (outtab$YLDG*wcy) # WCY parameter / fraction water in yield 
# outtab <- outtab %>%
#   mutate(PO = case_when(KLIMREG == 0 ~ "K",
#                         KLIMREG %in% c(1:3) ~ "R",
#                         KLIMREG %in% c(4:5) ~ "C",
#                         KLIMREG %in% c(6:7) ~ "B",
#                         KLIMREG %in% c(8:9) ~ "H"))

rm(acm)
rm(acy)
rm(phu_cal)
rm(outtab0)


# outtab == output tables; YLDG corrected with WCY parameter

```


\newpage 

# CULTIVARS REVIEW

## CULTIVARS

```{r TABLE OF CULTIVARS, results='asis'}

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";")
   # cat('\n')
   # cat("This is a heading for ", croplist[i] , "\n")
   # kable(cultivars, caption = paste0("Cultivars of ", cropname))
   # cat('\n')
   tab <- kable(cultivars, caption = paste0("Cultivars of ", cropname))
   print(tab)

```

## GRID 

```{r PLOT GRIDS}
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
plot(gridmap)
```


## MAP YIELD FOR ALL SCENARIOS

```{r YIELD MAPS FOR SCENARIOS, results='asis'}

out_scen <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, PRCP, PET, TS) %>% 
  group_by(runid) %>% 
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPRCP = mean(PRCP), 
            avgPET = mean(PET), avgTS = mean(TS)) %>% 
  distinct()

Lscen <- levels(as.factor(out_scen$scenario))
# print(Lscen)

if(crop == "BARL"){
    yld_lim <- c(2,7)
  } else if (crop == "CORN"){
    yld_lim <- c(0,11) # adjust
  } else if (crop == "WWHT"){
    yld_lim <- c(3,9)
  } else {
    print("ZEROO")
}

# for(i in 1:length(Lscen)) {  
for(i in Lscen) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- i
  filt_scen <- filter(out_scen, scenario == scene)
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID", all.x = T)
  ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
    geom_sf()+
    ggtitle(paste0("Average yield of ", cropname, " in 1989-2019 / scenario: ", scene )) + 
    scale_fill_gradient("[t/ha]", 
    low = "yellow",
    high = "darkgreen",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill", 
    limits = yld_lim)+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_yld)
}

```

## DESCRIPTIVE STATISTICS

descriptive statistics for each grid
calculated from all `r nrow(cultivars)` cultivars

```{r CROP YIELD STATS MAP}
destat <- outtab %>% 
select(runid, YR, scenario, GRID_NO, YLDG) %>% 
  group_by(GRID_NO) %>% 
  summarise(GRID_NO, minYLD = min(YLDG), maxYLD = max(YLDG),
            avgYLD = mean(YLDG), sdYLD = sd(YLDG)) %>% 
  mutate(ranYLD = maxYLD-minYLD) %>% 
  distinct()

# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)

desshp <-sp::merge(destat, gridmap, by.x = "GRID_NO", by.y = "GRID")

# mean

ggplot(desshp, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Mean simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                     high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# range

ggplot(desshp, aes(geometry = geometry, fill= ranYLD))+
  geom_sf()+
  ggtitle(paste0("Range of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# sd

ggplot(desshp, aes(geometry = geometry, fill= sdYLD))+
  geom_sf()+
  ggtitle(paste0("Standard deviation of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "red",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

```

\newpage 

# PLANTING, GERMINATION AND HARVEST DATE SHIFTS

criteria: 

* given IPLD and IPLD shift (0-2; 3-10; >10)

* IPLD and IGMD shift (0-5; 5-10; >10)

* given IHVD and IHVD shift (0-7; 7-14; >14)

working DF: **shifts**

working DF: **avg_shifts**


```{r PREPARING DF WITH CALCULATED DATE SHIFTS, message=FALSE}

# merge output table with designed cultivar

outtab <- if(crop == "WWHT"){
  filter(outtab, IHVD != 0)
} else {outtab <- outtab}


shifts <- outtab %>% 
  select(runid, YR, scenario, GRID_NO, YLDG, IPLD, IGMD, IHVD) %>% 
  merge(cultivars, by.x = "scenario", by.y = "runid") %>% 
  mutate(gIPLD = paste0(YR, sprintf("%02d", PLN_MON), sprintf("%02d", PLN_DAY))) %>% # given IPLD
  mutate(gIHVD = paste0(YR, sprintf("%02d", HRV_MON), sprintf("%02d", HRV_DAY))) # given IHVD
  

# formatting date

shifts$IPLD <- as.Date(as.character(shifts$IPLD), format = "%Y%m%d")
shifts$gIPLD <- as.Date(shifts$gIPLD, format = "%Y%m%d")

shifts$IGMD <- as.Date(as.character(shifts$IGMD), format = "%Y%m%d")

shifts$IHVD <- as.Date(as.character(shifts$IHVD), format = "%Y%m%d")
shifts$gIHVD <- as.Date(shifts$gIHVD, format = "%Y%m%d")


# differences 

shifts$shft_IPLD <- as.numeric(difftime(shifts$gIPLD, shifts$IPLD, units = "days"))
shifts$shft_IGMD <- as.numeric(difftime(shifts$IGMD, shifts$IPLD, units = "days"))
shifts$shft_IHVD <- as.numeric(difftime(shifts$gIHVD, shifts$IHVD, units = "days"))

if(seas == "WIN"){
  shifts$shft_IPLD <- case_when(shifts$shft_IPLD >= 365 ~ 0,
                                shifts$shft_IPLD != 365 ~ shifts$shft_IPLD)
} else {
  shifts$shft_IPLD <- shifts$shft_IPLD
}

# avg date shift for scenario

avg_shifts <- shifts %>% 
  group_by(runid) %>%
  summarise(runid, scenario, GRID_NO, avgYLD = mean(YLDG), avgPshft = mean(shft_IPLD), avgGshft = mean(shft_IGMD), 
            avgHshft = mean(shft_IHVD)) %>% # avgPRCP = mean(PRCP), avgPET = mean(PET), avgTS = mean(TS)
  distinct()
```

## IPLD

```{r IPLD SHIFT MAP}

if(crop == "BARL"){
    ipld_lim <- c(-30,30) # adjust
  } else if (crop == "CORN"){
    ipld_lim <- c(-60,30) 
  } else if (crop == "WWHT"){
    ipld_lim <- c(-10,10)
  } else {
    print("ZEROO")
}

for(i in 1:length(Lscen)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- Lscen[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IPLD <- ggplot(mout, aes(geometry = geometry, fill= avgPshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IPLD and actual IPLD for ", cropname, " / scenario: ", scene)) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = ipld_lim)+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IPLD)
}
```

## IGMD


```{r IGMD SHIFT MAP}

if(crop == "BARL"){
    igmd_lim <- c(-30,30) 
  } else if (crop == "CORN"){
    igmd_lim <- c(-60,30) # adjust
  } else if (crop == "WWHT"){
    igmd_lim <- c(-30,30)
  } else {
    print("ZEROO")
}

for(i in 1:length(Lscen)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- Lscen[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgGshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of IGMD from IPLD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = igmd_lim)+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

## IHVD

```{r IHVD SHIFT MAP}

if(crop == "BARL"){
    ihvd_lim <- c(-30,30) # adjust
  } else if (crop == "CORN"){
    ihvd_lim <- c(-100,10) 
  } else if (crop == "WWHT"){
    ihvd_lim <- c(-5,5)
  } else {
    print("ZEROO")
}

for(i in 1:length(Lscen)) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- Lscen[i]
  filt_scen <- filter(avg_shifts, scenario == scene)
  # gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
  gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, gridmap, by.x = "GRID_NO", by.y = "GRID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgHshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IHVD and actual IHVD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = ihvd_lim)+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

\newpage

# SELECTING SCENARIO

## BASED ON IPLD

```{r SCENARIO BASED ON IPLD TAB}

selIPLD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgPshft)))
 
selIPLD$scenario <- as.factor(selIPLD$scenario)
summary(selIPLD$scenario)


cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIPLD$scenario

IPLD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IPLD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IPLD"))
print(tab)
```


```{r SCENARIO BASED ON IPLD MAP}

# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIPLD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IPLD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)

```

## BASED ON IGMD

```{r SCENARIO BASED ON IGMD TAB}

selIGMD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgGshft)))
 

selIGMD$scenario <- as.factor(selIGMD$scenario)
summary(selIGMD$scenario)


cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIGMD$scenario

IGMD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IGMD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IGMD"))
print(tab)
```

```{r SCENARIO BASED ON IGMD MAP}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIGMD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IGMD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```

## BASED ON IHVD

```{r SCENARIO BASED ON IHVD TAB}

selIHVD <- avg_shifts %>% 
  group_by(GRID_NO) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgHshft)))
 

selIHVD$scenario <- as.factor(selIHVD$scenario)
summary(selIHVD$scenario)


cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ";") 
   
sel_scen <- selIHVD$scenario

IHVD_sel <- cultivars %>% 
  filter(runid %in% sel_scen)
tab <- kable(IHVD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IHVD"))
print(tab)
```

```{r SCENARIO BASED ON IHVD MAP}
# gridmap <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T) # CZ
gridmap <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
mout <-sp::merge(selIHVD, gridmap, by.x = "GRID_NO", by.y = "GRID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IHVD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```



```{r RENDER, eval=F}

# install.packages("rmarkdown")
# library(rmarkdown)
# rmarkdown::render(input = "EPIC_hrvCult.Rmd", 
#        output_format = "pdf_document",
#        output_file = paste0("c:/Users/krizovak/Documents/__EPIC__/R/markdown/reports/", crop, "_hrvCultReport.pdf"))

```

