---
title: "EPIC harvest Cultivars - parallelized"
author: "Katerina Krizova"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:  
  pdf_document:
    toc: yes
    toc_depth: 3
 
---

\newpage 

```{r SETUP, include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, fig.dim = c(9, 5))

# install.packages("tidyverse", dependencies = T)
# install.packages("gdata")
require(tidyverse)
# require(data.table)
require(gdata) # write.fwf
library(sf)
library(sp)
library(rgdal)
require(reshape2)
require(ggpubr)
library(knitr)
```

# INITIAL SETUP

## crop params

```{r CROP PARAMETERS}

runspec <- "n0"

# crop <- "ALFA"
# crop <- "BARL"
# crop <- "CSIL"
crop <- "CORN"
# crop <- "OATS"
# crop <- "FPEA"
# crop <- "POTA"
# crop <- "RAPE"
# crop <- "RYE"
# crop <- "SGBT"
# crop <- "SUNF"
# crop <- "SOYB"
# crop <- "WWHT"

# crop ID + seasonality

if(crop == "ALFA"){
    cropid <- 31 
    cropname <- "alfalfa"
    seas <- "OTH"
  } else if (crop == "BARL"){
    cropid <- 14
    cropname <- "spring barley"
    seas <- "SPG"
  } else if (crop == "CSIL"){
    cropid <- 29
    cropname <- "corn silage"
    seas <- "SPG"
  } else if (crop == "CORN"){
    cropid <- 2
    cropname <- "corn"
    seas <- "SPG"
  } else if (crop == "OATS"){
    cropid <- 16
    cropname <- "oat"
    seas <- "SPG"
  } else if (crop == "FPEA"){
    cropid <- 26
    cropname <- "field peas"
    seas <- "SPG"
  } else if (crop == "POTA"){
    cropid <- 51
    cropname <- "potatoes"
    seas <- "SPG"
  } else if (crop == "RAPE"){
    cropid <- 122
    cropname <- "winter rapeseed"
    seas <- "WIN"
  } else if (crop == "RYE") {
    cropid <- 19
    cropname <- "rye"
    seas <- "WIN"
  } else if (crop == "SGBT"){
    cropid <- 62
    cropname <- "sugarbeet"
    seas <- "SPG"
  } else if (crop == "SUNF"){
    cropid <- 7
    cropname <- "sunflower"
    seas <- "SPG"
  } else if (crop == "SOYB"){
    cropid <- 1
    cropname <- "soybean"
    seas <- "SPG"
  } else if (crop == "WWHT"){
    cropid <- 10
    cropname <- "winter wheat"
    seas <- "WIN"
  } else {
    print("ZEROO")
}

# WCY parameter (fraction water in yield ) WCY = 0.12 -> yield + wcy -> 1.12

# ??? RAPE ???

wcy <- case_when(crop %in% c("ALFA", "BARL", "FPEA", "RYE", "WWHT") ~ 1.12,
                 crop %in% c("CSIL", "CORN") ~ 1.15, 
                 crop %in% c("OATS") ~ 1.10, 
                 crop %in% c("POTA") ~ 1.8, 
                 crop %in% c("SGBT") ~ 1.84, 
                 crop %in% c("SUNF") ~ 1.06, 
                 crop %in% c("SOYB") ~ 1.13) 

epic_parall <- c(1:8)
```

## paths 

```{r SET PATHS + BACKUP REPORT, echo = T}

path_in <- "c:/Users/krizovak/Documents/__EPIC__/R/" 

path_met <- "C:/Users/krizovak/Documents/__EPIC__/R/_tables/v3_czsk/" 
path_epic <- "c:/Users/krizovak/Documents/__EPIC__/EPIC_CS_v4_Aug2022/" 

path_tab <- "c:/Users/krizovak/Documents/__EPIC__/R/_tables/" 
path_shp <- "c:/Users/krizovak/Documents/__EPIC__/R/_shapefiles/" 

path_out <- "c:/Users/krizovak/Documents/__EPIC__/R/_nitroRESULTS/" 

# REPORT COPY

report <- "C:/Users/krizovak/Documents/__EPIC__/R/markdown/__epicRMD/PARALL_hrvCult.pdf"

if (file.exists(report)){
  print("File exists!")
  mtime <- file.info(report)$mtime
  # mtime <- as.Date(mtime, format=c('y-m-d','h-m-s'))
  # mtime <- as.POSIXlt(mtime)
  mtime <- format(mtime,format='%Y%m%d-%H%M%S')
  path_old <- "C:/Users/krizovak/Documents/__EPIC__/R/markdown/__epicRMD/"
  path_new <- paste0(path_out, crop, "/_outs/_reports/")
  file.rename(from = paste0(path_old, "PARALL_hrvCult.pdf"), 
              to = paste0(path_new, "PARALL_hrvCult_", mtime, ".pdf"))
} else {
  print("File does not exist!")
}
```

## time period

```{r SET TIME PERIOD, echo = T}
period <- 1989:2019 
```


* crop: `r crop`

* crop ID: `r cropid`

* crop name: `r cropname`

* seasonality: `r seas`

* WCY parameter: `r wcy`

\newpage

# SPATIAL REFERENCE

```{r PLOT GRIDS}
czsk_shp <- st_read(paste0(path_shp, "CS_CGMS10k_SpatRef_v0.shp"), crs = 5514, quiet = T) # CZ i SK crs = 5514, 
plot(czsk_shp)
```

* total GRIDS: `r nrow(czsk_shp)`


\newpage 

# HARVEST OUTPUT FILES

Steps for AFTER simulation:

## COPY AND PASTE ACM AND ACY

EPIC output files are stored in **EPIC_CS_X/EPIC0810** folder

Backup files:

* create a folder '_outs' in cultivar results folder

* create a subfolder 'crop_outs_runspec' in '_outs' folder

* copy all files in both newly created folders, so that: 

  + there is a backup in date-named folder
  
  + there are always the latest ACM and ACY files to be further worked with

```{r COPY ACM AND ACY, include=F}

# batch

for(i in 1:length(epic_parall)) {
  dir.create(paste0(path_out, crop, "/_outs/outs_", runspec), showWarnings = FALSE) #showWarnings = FALSE -> folder is not overwritten, files copied into the firstly created one
  path_source <- paste0(path_epic,"EPIC_CS_", i, "/EPIC0810/")
  Louts <- list.files(path_source, pattern = ".ACM|.ACY") # pattern either ACM or ACY (only AC was not enough because of WORKSPACE file)
  newDir <- paste0(path_out, crop, "/_outs/outs_", runspec, "/")
  newDir2 <- paste0(path_out, crop, "/_outs/")
  file.copy(from = paste0(path_source, Louts),   # Output files backup in folder with date
          to = paste0(newDir, Louts))
  file.copy(from = paste0(path_source, Louts),   # Latest ouptut files in '_outs' folder
          to = paste0(newDir2, Louts), overwrite = TRUE)
}


# ACM and ACY files are deleted befor a new run (EPIC_runCult.Rmd)

# # !!! FINAL !!! FINAL !!! FINAL !!!
# for(i in 1:length(epic_parall)) {
#   path_source <- paste0(path_epic,"EPIC_CS_", i, "/EPIC0810/")
#   Louts <- list.files(path_source, pattern = ".ACM|.ACY")
#   file.remove(paste0(path_source, Louts)) # ACM and ACY files removal from EPIC0810 folder
# }
# # !!! FINAL !!! FINAL !!! FINAL !!!

# single 

# currentDate <- Sys.Date()
dir.create(paste0(path_out, crop, "/_outs/outs_", runspec), showWarnings = FALSE) #showWarnings = FALSE -> folder is not overwritten, files copied into the firstly created one
path_source <- paste0(path_epic,"EPIC_CS_4/EPIC0810/")
Louts <- list.files(path_source, pattern = ".ACM|.ACY") # pattern either ACM or ACY (only AC was not enough because of WORKSPACE file)
newDir <- paste0(path_out, crop, "/_outs/outs_", runspec, "/")
newDir2 <- paste0(path_out, crop, "/_outs/")
file.copy(from = paste0(path_source, Louts),   # Output files backup in folder with date
          to = paste0(newDir, Louts))
file.copy(from = paste0(path_source, Louts),   # Latest ouptut files in '_outs' folder
          to = paste0(newDir2, Louts), overwrite = TRUE)

# remove files and paths

rm(path_source)
rm(Louts)
rm(newDir)
rm(newDir2)

```

## ACM HARVEST

*Annual cropman file*

Variable / Description / Units  
Y = Year  
RT# = Rotation number  
PRCP = Precipitation mm  
ET = Potential evapotranspiration mm  
ET = Evapotranspiration mm  
Q = Runoff mm  
SSF = Subsurface flow mm  
PRK = Percolation mm  
CVF = MUSLE crop cover factor  
MUSS = Water erosion T/ha  
YW = Wind erosion T/ha  
GMN = N mineralized kg/ha  
NMN = Humus mineralization kg/ha  
NFIX = Nitrogen fixation kg/ha  
NITR = Nitrification kg/ha  
AVOL = Nitrogen volatilization kg/ha  
DN = Denitrification kg/ha  
YON = Nitrogen loss with sediment kg/ha  
QNO3 = Nitrate loss in surface runoff kg/ha  
SSFN = Nitrogen in subsurface flow kg/ha  
PRKN = Nitrogen loss in percolate kg/ha  
MNP = Phosphorus mineralized kg/ha  
YP = Phosphorus loss in sediment kg/ha  
QAP = Labile phosphorus loss in runoff kg/ha  
PRKP = Phosphorus loss in percolate kg/ha  
LIME = Lime applied kg/ha  
OCPD = Organic carbon in plow layer depth set by PARM(16) kg/ha  
TOC = Organic carbon in soil profile kg/ha  
APBC = Labile phosphorus content in plow layer %  
TAP = Total labile p in soil profile kg/ha  
TNO3 = Total nitrate in soil profile kg/ha  

```{r ACM HARVEST, eval=T}

# load ACM files without 11 lines of header, combine into a single df

acmnames <- list.files(paste0(path_out, crop, "/_outs/"), pattern= "\\.ACM$")  # Identify file names

acm_comb = data.frame() # empty dataframe to write ACM files in

for(i in acmnames) { # TAKES AGES !!
  a <- read.table(paste0(path_out, crop, "/_outs/", i), header = FALSE, skip = 11)
  a$source <- paste0(i)
  a$source <- str_sub(a$source,1,nchar(a$source)-4)
  df <- data.frame(a) 
  acm_comb <- rbind(acm_comb, df)
}

# rename header

col_names_acm <- c("YR",  "RT", "PRCP", "PET", "ET ", "Q", "SSF", "PRK", "CVF", "MUSS", "YW", "GMN", "NMN", "NFIX", "NITR", "AVOL",
                   "DN", "YON", "QNO3", "SSFN", "PRKN", "MNP", "YP", "QAP", "PRKP", "LIME", "OCPD", "TOC", "APBC", "TAP", "TNO3", "runid")
names(acm_comb) <- col_names_acm
# names(acm) <- col_names_acm


# *** WR *** WR *** WR ** WR ***
# currentDate <- Sys.Date()
write.csv(acm_comb, file = paste0(path_out, crop, "/_outs/acm.csv"), row.names=FALSE)
write.csv(acm_comb, file = paste0(path_out, crop, "/_outs/outs_", runspec,"/", runspec
                                 , "_", crop, "_acm.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***

```

## ACY HARVEST

*Annual Crop Yield*

Variable / Description / Units  
Y = Year  
RT# = Fertilizer ID  
CPNM = Crop name  
YLDG = Grain yield T/ha  
YLDF = Forage yield T/ha  
BIOM Biomass T/ha  
YLN = Nitrogen used by crop kg/ha  
YLP = Phosphorus used by crop kg/ha  
FTN = Nitrogen applied kg/ha  
FTP = Phosphorus applied kg/ha  
IRGA = Irrigation volume applied mm  
IRDL = Irrigation water lost in delivery system mm  
WUEF = Water use efficiency (crop yield / growing season ET) kg/mm  
GSET = Growing season et (mm) mm  
CAW = Crop available water (soil water at planting + growing season rainfall - runoff) mm  
CRF = Growing season rainfall mm  
CQV = Growing season runoff mm  
COST = Cost of production $/ha  
COOP = Operating cost $/ha  
RYLG = Return for grain yield $/ha  
RYLF = Return for forage yield $/ha  
PSTF = Pest damage factor (fraction of yield remaining after pest damage  
WS = Water stress days d/yr  
NS = Nitrogen stress days d/yr  
PS = Phosphorus stress days d/yr  
KS = Potassium stress days d/yr  
TS = Temperature stress days d/yr  
AS = Aeration stress days d/yr  
SS = Salinity stress factor  
PPOP = Plant population plants/m2  
IPLD = Planting date  
IGMD = Germination date  
IHVD = Harvest date  

```{r ACY HARVEST, eval=T}

# load ACY files without 11 lines of header and a single file

acynames <- list.files(paste0(path_out, crop, "/_outs/"), pattern= "\\.ACY$")   # Identify file names

acy_comb = data.frame() # empty dataframe to write ACM files in

for(i in acynames) { # TAKES AGES !!
  a <- read.table(paste0(path_out, crop, "/_outs/", i), header = FALSE, skip = 11)
  a$source <- paste0(i)
  a$source <- str_sub(a$source,1,nchar(a$source)-4)
  df <- data.frame(a) 
  acy_comb <- rbind(acy_comb, df)
}

# rename header

col_names_acy <- c("YR",  "RT", "CPNM", "YLDG", "YLDF", "WCYD", "HI", "BIOM", "RW", 
                   "YLN", "YLP", "YLC", "FTN", "FTP", "IRGA", "IRDL", "WUEF", "GSET", 
                   "CAW", "CRF", "CQV", "COST", "COOP", "RYLG", "RYLF", "PSTF", 
                   "WS", "NS", "PS", "KS", "TS", "AS", "SS", "PPOP", 
                   "IPLD", "IGMD", "IHVD", "runid")
names(acy_comb) <- col_names_acy
names(acy_comb) <- col_names_acy


# *** WR *** WR *** WR ** WR ***
# currentDate <- Sys.Date()
write.csv(acy_comb, file = paste0(path_out, crop, "/_outs/acy.csv"), row.names=FALSE)
write.csv(acy_comb, file = paste0(path_out, crop, "/_outs/outs_", runspec,"/",
                                 runspec, "_", crop, "_acy.csv"), row.names=FALSE)
# *** WR *** WR *** WR ** WR ***


rm(a)
rm(df)
rm(acm_comb)
rm(acy_comb)
```


## OUTPUT TABLE

ACM and ACY tables combined in one  
Contains all important outputs of the simulation

```{r OUTPUT TABLE}

# *** READ *** READ *** READ ** READ ***
phu_cal_PAR <- read.table(paste0(path_out, crop, "/", crop, "_phu_cal_PAR.csv"), header = TRUE, sep = ";")
cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ",")

acm <- read.table(paste0(path_out, crop, "/_outs/acm.csv"), header = T, sep = ",")
acy <- read.table(paste0(path_out, crop, "/_outs/acy.csv"), header = T, sep = ",")

# OR ?
  
# if (seas == "SPG"){
#   acm <- read.table(paste0(path_out, crop, "//_outs/acm.csv"), header = T, sep = ",")
#   acy <- read.table(paste0(path_out, crop, "//_outs/acy.csv"), header = T, sep = ",")
# }  else if (seas == "WIN"){
#   acm <- read.table(paste0(path_out, crop, "//_outs/acm.csv"), header = T, sep = ",") %>%
#   filter(YR != 1989)
#   acy <- read.table(paste0(path_out, crop, "//_outs/acy.csv"), header = T, sep = ",") %>%
#   filter(IHVD != 0)
# } else {
#   print("ZEROO")
#   
# }
# *** READ *** READ *** READ ** READ ***

# manage WIN crops

# merge ACM and ACY; apply WCY parameter

outtab0 <- merge(acm, acy)
outtab <- merge(outtab0, phu_cal_PAR, by.x = "runid", by.y = "runid") %>% # join ACM and ACY with SCENARIO
  mutate(SC_TYP = case_when(str_detect(scenario, "1") ~ 1,
                        str_detect(scenario, "2") ~ 2,
                        str_detect(scenario, "3") ~ 3))
outtab$YLDG <- (outtab$YLDG*wcy) # WCY parameter / fraction water in yield 

rm(acm)
rm(acy)
rm(phu_cal_PAR)
rm(outtab0)


# outtab == output tables; YLDG corrected with WCY parameter


# JOIN outtab AND CZSK SHAPEFILE FOR ALL RES PARAMS VISUALISATIONS

result_map <- merge(czsk_shp, outtab, by.x = "CGMS_ID", by.y = "GRID", all.x = T)

```
  
\newpage  

# CULTIVARS REVIEW

## CULTIVARS

```{r TABLE OF CULTIVARS, results='asis'}

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ",")
   # cat('\n')
   # cat("This is a heading for ", croplist[i] , "\n")
   # kable(cultivars, caption = paste0("Cultivars of ", cropname))
   # cat('\n')
   tab <- kable(cultivars, caption = paste0("Cultivars of ", cropname))
   print(tab)

```


```{r PHU+DATES MAP}

# PHU MAP

result_map$PHU <- round(result_map$PHU, 0)

phu_map <- result_map %>% 
  select(CGMS_ID, YR, PHU, geometry) %>% 
  filter(YR == 2000) %>% 
  distinct()

ggplot(phu_map, aes(geometry = geometry, fill= PHU))+ 
  geom_sf()+
  # geom_sf_label(aes(label = PHU))+
  # geom_sf_text(aes(label = PHU), colour = "white", size = 1.5, fontface = "bold")+
  ggtitle(paste0("Average PHU for ", crop, " in 1989-2019")) + 
  scale_fill_gradient("", 
    low = "yellow",
    # mid = "green",
    high = "darkmagenta",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
 
# ggsave(paste0(path_out, crop, "/", crop, "_map_avgPHU.jpg"), width = 30, height = 20, units = "cm")

rm(phu_map)

# DATES MAPS

dates_map <- result_map %>% 
  select(CGMS_ID, YR, scenario, SC_TYP, PLN_JUL, HRV_JUL, LVP, geometry) %>% 
  filter(YR == 2000) %>% 
  distinct()

# PLN 

for(i in 1:3){
  a <- dates_map %>% filter(SC_TYP == i)
  gp <- ggplot(a, aes(geometry = geometry, fill= PLN_JUL))+ 
    geom_sf()+
    # geom_sf_label(aes(label = PHU))+
    # geom_sf_text(aes(label = PLN_JUL), colour = "white", size = 1.5, fontface = "bold")+
    ggtitle(paste0("Planting day (julian) for ", crop, " / scenario:", i)) + 
    scale_fill_gradient("", 
                        low = "forestgreen",
                        # mid = "green",
                        high = "red",
                        space = "Lab",
                        na.value = "grey50",
                        guide = "colourbar",
                        aesthetics = "fill")+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
          axis.ticks.y = element_blank(), axis.text.y = element_blank(),
          plot.title = element_text(hjust = 0.5))
  print(gp)
}

# HRV

for(i in 1:3){
  a <- dates_map %>% filter(SC_TYP == i)
  gh <- ggplot(a, aes(geometry = geometry, fill= HRV_JUL))+ 
    geom_sf()+
    # geom_sf_label(aes(label = PHU))+
    # geom_sf_text(aes(label = HRV_JUL), colour = "white", size = 1.5, fontface = "bold")+
    ggtitle(paste0("Harvesting day (julian) for ", crop, " / scenario:", i)) + 
    scale_fill_gradient("", 
                        low = "gold",
                        # mid = "green",
                        high = "red",
                        space = "Lab",
                        na.value = "grey50",
                        guide = "colourbar",
                        aesthetics = "fill")+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
          axis.ticks.y = element_blank(), axis.text.y = element_blank(),
          plot.title = element_text(hjust = 0.5))
  print(gh)
}

# LVP

for(i in 1:3){
  a <- dates_map %>% filter(SC_TYP == i)
  gl <- ggplot(a, aes(geometry = geometry, fill = LVP))+ 
    geom_sf()+
    # geom_sf_label(aes(label = PHU))+
    # geom_sf_text(aes(label = LVP), colour = "white", size = 1.5, fontface = "bold")+
    ggtitle(paste0("Length of vegetation period for ", crop, " / scenario:", i)) + 
    scale_fill_gradient("days", 
                        low = "cyan4",
                        # mid = "green",
                        high = "darkblue",
                        space = "Lab",
                        na.value = "grey50",
                        guide = "colourbar",
                        aesthetics = "fill")+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
          axis.ticks.y = element_blank(), axis.text.y = element_blank(),
          plot.title = element_text(hjust = 0.5))
  print(gl)
}

rm(dates_map)
rm(a)
rm(gp)
rm(gh)
rm(gl)

```


\newpage

## MAP YIELD FOR ALL SCENARIOS

```{r YIELD MAPS FOR SCENARIOS, results='asis'}


if(crop == "BARL"){
    yld_lim <- c(2,8)
  } else if (crop == "CORN"){
    yld_lim <- c(0,11) # adjust
  } else if (crop == "WWHT"){
    yld_lim <- c(3,9)
  } else {
    print("ZEROO")
}

yield_map <- result_map %>% 
  select(CGMS_ID, YR, scenario, SC_TYP, YLDG, geometry) %>% 
  group_by(CGMS_ID, scenario) %>% 
  mutate(aYLDG = mean(YLDG)) %>%
  select(-YR, -YLDG)


for(i in 1:3) {  
  a <- yield_map %>% filter(SC_TYP == i)
  gy <- ggplot(yield_map, aes(geometry = geometry, fill= aYLDG))+
    geom_sf()+
    ggtitle(paste0("Average yield of ", cropname, " in 1989-2019 / scenario: ", i )) + 
    scale_fill_gradient("[t/ha]", 
    low = "yellow",
    high = "darkgreen",
    # limits = yld_lim,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(gy)
}

rm(yield_map)
rm(a)
rm(gy)

```
\newpage

## METEOROLOGICAL MAPS

```{r METEO STRESS MAPS}

met_map <- result_map %>% 
  select(CGMS_ID, YR, scenario, SC_TYP, PRCP, PET, ET., TS, WS, NS, geometry) %>% 
  group_by(CGMS_ID, scenario) %>% 
  mutate(aPRCP = mean(PRCP)) %>%
  mutate(aPET = mean(PET)) %>%
  mutate(aET = mean(ET.)) %>% 
  mutate(ETPET = ET./PET) %>% 
  mutate(aETPET = mean(ETPET)) %>% 
  mutate(aTS = mean(TS)) %>% 
  mutate(aWS = mean(WS)) %>% 
  mutate(aNS = mean(NS))

# PRCP

gpr <- ggplot(met_map, aes(geometry = geometry, fill= aPRCP))+
  geom_sf()+
  ggtitle(paste0("Average rainfall in 1989-2019 ")) + 
  scale_fill_gradient("[mm]", 
                      low = "lightblue",
                      high = "darkblue",
                      # limits = yld_lim,
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+ 
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(gpr)

# PET

gpe <- ggplot(met_map, aes(geometry = geometry, fill= aPET))+
  geom_sf()+
  ggtitle(paste0("Average PET in 1989-2019 ")) + 
  scale_fill_gradient("[mm]", 
                      low = "lightblue",
                      high = "darkblue",
                      # limits = yld_lim,
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+ 
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(gpe)
  
```


## STRESS MAPS

- scenario-specific factors  

```{r SCEN-SPEC MAPS}

# ET/PET

for(i in 1:3) {  
  a <- met_map %>% filter(SC_TYP == i)
  ge <- ggplot(met_map, aes(geometry = geometry, fill= aETPET))+
    geom_sf()+
    ggtitle(paste0("Average ET/PET in 1989-2019 / scenario: ", i )) + 
    scale_fill_gradient("[]", 
    low = "lightblue",
    high = "darkblue",
    # limits = yld_lim,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ge)
}

# TS

for(i in 1:3) {  
  a <- met_map %>% filter(SC_TYP == i)
  gt <- ggplot(met_map, aes(geometry = geometry, fill= aTS))+
    geom_sf()+
    ggtitle(paste0("Average temperature stress in 1989-2019 / scenario: ", i )) + 
    scale_fill_gradient("[days]", 
    low = "yellow",
    high = "red",
    # limits = yld_lim,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(gt)
}

# WS

for(i in 1:3) {  
  a <- met_map %>% filter(SC_TYP == i)
  gw <- ggplot(met_map, aes(geometry = geometry, fill= aWS))+
    geom_sf()+
    ggtitle(paste0("Average water stress in 1989-2019 / scenario: ", i )) + 
    scale_fill_gradient("[days]", 
    low = "lightblue",
    high = "red",
    # limits = yld_lim,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(gw)
}

# NS

for(i in 1:3) {  
  a <- met_map %>% filter(SC_TYP == i)
  gn <- ggplot(met_map, aes(geometry = geometry, fill= aNS))+
    geom_sf()+
    ggtitle(paste0("Average nitrogen stress in 1989-2019 / scenario: ", i )) + 
    scale_fill_gradient("[days]", 
    low = "chartreuse",
    high = "brown",
    # limits = yld_lim,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill")+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(gn)
}

```


\newpage 

# PLANTING, GERMINATION AND HARVEST DATE SHIFTS

criteria: 

* given IPLD and IPLD shift (0-2; 3-10; >10)

* IPLD and IGMD shift (0-5; 5-10; >10)

* given IHVD and IHVD shift (0-7; 7-14; >14)

working DF: **shifts**

working DF: **avg_shifts**


```{r PREPARING DF WITH CALCULATED DATE SHIFTS, message=FALSE}

# merge output table with designed cultivar

outtab <- if(crop == "WWHT"){
  filter(outtab, IHVD != 0)
} else {outtab <- outtab}


shifts <- outtab %>% 
  select(runid, YR, scenario, VO_TYP, GRID, YLDG, IPLD, IGMD, IHVD) %>% 
  merge(cultivars, by.x = "scenario", by.y = "CULT") %>% 
  mutate(gIPLD = paste0(YR, sprintf("%02d", PLN_MON), sprintf("%02d", PLN_DAY))) %>% # given IPLD
  mutate(gIHVD = paste0(YR, sprintf("%02d", HRV_MON), sprintf("%02d", HRV_DAY))) %>%  # given IHVD
  mutate(var_scen = case_when(scenario %in% c("k1", "r1", "b1", "h1") ~ 1,
                              scenario %in% c("k2", "r2", "b2", "h2") ~ 2,
                              scenario %in% c("k3", "r3", "b3", "h3") ~ 3))

# formatting date

shifts$IPLD <- as.Date(as.character(shifts$IPLD), format = "%Y%m%d")
shifts$gIPLD <- as.Date(shifts$gIPLD, format = "%Y%m%d")

shifts$IGMD <- as.Date(as.character(shifts$IGMD), format = "%Y%m%d")

shifts$IHVD <- as.Date(as.character(shifts$IHVD), format = "%Y%m%d")
shifts$gIHVD <- as.Date(shifts$gIHVD, format = "%Y%m%d")


# differences 

shifts$shft_IPLD <- as.numeric(difftime(shifts$gIPLD, shifts$IPLD, units = "days"))
shifts$shft_IGMD <- as.numeric(difftime(shifts$IGMD, shifts$IPLD, units = "days"))
shifts$shft_IHVD <- as.numeric(difftime(shifts$gIHVD, shifts$IHVD, units = "days"))

if(seas == "WIN"){
  shifts$shft_IPLD <- case_when(shifts$shft_IPLD >= 365 ~ 0,
                                shifts$shft_IPLD != 365 ~ shifts$shft_IPLD)
} else {
  shifts$shft_IPLD <- shifts$shft_IPLD
}

# avg date shift for scenario

avg_shifts <- shifts %>% 
  group_by(runid) %>%
  summarise(runid, scenario, var_scen, GRID, avgYLD = mean(YLDG), avgPshft = mean(shft_IPLD), avgGshft = mean(shft_IGMD), 
            avgHshft = mean(shft_IHVD)) %>% # avgPRCP = mean(PRCP), avgPET = mean(PET), avgTS = mean(TS)
  distinct()
```

## IPLD

```{r IPLD SHIFT MAP}

if(crop == "BARL"){
    ipld_lim <- c(-25,10) # adjust
  } else if (crop == "CORN"){
    ipld_lim <- c(-30,10) 
  } else if (crop == "WWHT"){
    ipld_lim <- c(-20,50)
  } else {
    print("ZEROO")
}

for(i in 1:3) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- i
  filt_scen <- filter(avg_shifts, var_scen == scene)
  # czsk_shp <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")
  ggp_IPLD <- ggplot(mout, aes(geometry = geometry, fill= avgPshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IPLD and actual IPLD for ", cropname, " / scenario: ", scene)) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = ipld_lim)+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IPLD)
}
```

## IGMD


```{r IGMD SHIFT MAP}

if(crop == "BARL"){
    igmd_lim <- c(0,20) 
  } else if (crop == "CORN"){
    igmd_lim <- c(0,30) # adjust
  } else if (crop == "WWHT"){
    igmd_lim <- c(0,40)
  } else {
    print("ZEROO")
}

for(i in 1:3) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- i
  filt_scen <- filter(avg_shifts, var_scen == scene)
  # czsk_shp <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgGshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of IGMD from IPLD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = igmd_lim)+
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

## IHVD

```{r IHVD SHIFT MAP}

if(crop == "BARL"){
    ihvd_lim <- c(-30,10) # adjust
  } else if (crop == "CORN"){
    ihvd_lim <- c(-80,0) 
  } else if (crop == "WWHT"){
    ihvd_lim <- c(-10,0)
  } else {
    print("ZEROO")
}

for(i in 1:3) {  
  # pick_scen <- read.table(paste0(path_out, crop, "/", crop, "_selectedScen.csv"), header = T, sep = ";")
  scene <- i
  filt_scen <- filter(avg_shifts, var_scen == scene)
  # czsk_shp <- st_read(paste0(path_shp, "EEA_CZSK_10km_n1427_5514.shp"), crs = 5514, quiet = T) # CZ i SK
  mout <-sp::merge(filt_scen, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")
  ggp_IGMD <- ggplot(mout, aes(geometry = geometry, fill= avgHshft))+
    geom_sf()+
    ggtitle(paste0("Average shift of given IHVD and actual IHVD for ", cropname, " / scenario: ", scene )) + 
    scale_fill_gradient2("[days]", 
    low = "red",
    mid = "green",
    high = "blue",
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill",
    limits = ihvd_lim)+ 
    coord_sf()+
    theme_void()+
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
  print(ggp_IGMD)
}
```

\newpage

# SELECTING SCENARIO

## BASED ON IPLD

```{r SCENARIO BASED ON IPLD TAB, results='asis', eval=F}


selIPLD <- avg_shifts %>% 
  group_by(GRID) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgPshft)))
 
selIPLD$scenario <- as.factor(selIPLD$scenario)
summary(selIPLD$scenario)


cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ",") 
   
sel_scen <- selIPLD$scenario

IPLD_sel <- cultivars %>% 
  filter(CULT %in% sel_scen)
tab <- kable(IPLD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IPLD"))
print(tab)
```


```{r SCENARIO BASED ON IPLD MAP, eval=F}

mout <-sp::merge(selIPLD, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IPLD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)

```

## BASED ON IGMD

```{r SCENARIO BASED ON IGMD TAB, results='asis', eval=F}

selIGMD <- avg_shifts %>% 
  group_by(GRID) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgGshft)))
 

selIGMD$scenario <- as.factor(selIGMD$scenario)
summary(selIGMD$scenario)


cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ",") 
   
sel_scen <- selIGMD$scenario

IGMD_sel <- cultivars %>% 
  filter(CULT %in% sel_scen)
tab <- kable(IGMD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IGMD"))
print(tab)
```

```{r SCENARIO BASED ON IGMD MAP, eval=F}

mout <-sp::merge(selIGMD, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IGMD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```

## BASED ON IHVD

```{r SCENARIO BASED ON IHVD TAB, results='asis', eval=F}

selIHVD <- avg_shifts %>% 
  group_by(GRID) %>%
  # filter(H == min(H)) %>% 
  # filter(P == min(P)) 
  # filter(HPsum == min(HPsum)) 
  slice(which.min(abs(avgHshft)))
 

selIHVD$scenario <- as.factor(selIHVD$scenario)
sum <- summary(selIHVD$scenario)

cultivars <- read.table(paste0(path_out, crop, "/", crop, "_cultivars.csv"), header = TRUE, sep = ",") 
   
sel_scen <- selIHVD$scenario

IHVD_sel <- cultivars %>% 
  filter(CULT %in% sel_scen)
tab <- kable(IHVD_sel, caption = paste0("Selected cultivars of ", cropname, " based on IHVD"))
print(tab)
```

```{r SCENARIO BASED ON IHVD MAP, eval=F}

mout <-sp::merge(selIHVD, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")

# yield

ggp_yld <- ggplot(mout, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Average yield of ", cropname, " in 1989-2019")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_yld)

# scenarios

ggp_scen <- ggplot(mout, aes(geometry = geometry, fill= scenario))+
  geom_sf()+
  ggtitle(paste0("Selected planting scenarios for ", cropname, " based on IHVD")) + 
  # scale_fill_gradient("[t/ha]", 
  #                     low = "yellow",
  #                     high = "darkgreen",
  #                     space = "Lab",
  #                     na.value = "grey50",
  #                     guide = "colourbar",
  #                     aesthetics = "fill")+
  #                     # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(ggp_scen)
```


```{r DO NOT RUN, eval=F}

# install.packages("rmarkdown")
# library(rmarkdown)
# rmarkdown::render(input = "EPIC_hrvCult.Rmd", 
#        output_format = "pdf_document",
#        output_file = paste0("c:/Users/krizovak/Documents/__EPIC__/R/markdown/reports/", crop, "_hrvCultReport.pdf"))

destat <- outtab %>% 
select(runid, YR, scenario, GRID, YLDG) %>% 
  group_by(GRID) %>% 
  summarise(GRID, minYLD = min(YLDG), maxYLD = max(YLDG),
            avgYLD = mean(YLDG), sdYLD = sd(YLDG)) %>% 
  mutate(ranYLD = maxYLD-minYLD) %>% 
  distinct()

# czsk_shp <- st_read(paste0(path_shp, "10km_simu_5514.shp"), crs = 5514, quiet = T)

desshp <-sp::merge(destat, czsk_shp, by.x = "GRID", by.y = "CGMS_ID")

# mean

ggplot(desshp, aes(geometry = geometry, fill= avgYLD))+
  geom_sf()+
  ggtitle(paste0("Mean simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "yellow",
                     high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# range

ggplot(desshp, aes(geometry = geometry, fill= ranYLD))+
  geom_sf()+
  ggtitle(paste0("Range of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "darkgreen",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

# sd

ggplot(desshp, aes(geometry = geometry, fill= sdYLD))+
  geom_sf()+
  ggtitle(paste0("Standard deviation of simulated yield")) + 
  scale_fill_gradient("[t/ha]", 
                      low = "lightblue",
                      high = "red",
                      space = "Lab",
                      na.value = "grey50",
                      guide = "colourbar",
                      aesthetics = "fill")+
                      # limits = c(4.7,7.1))+
  coord_sf()+
  theme_void()+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), 
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5))


```

